### 2020-12-04 report/article.tex
🎉 Add basic setup with Austin's subfile.

\documentclass[11pt]{article}
\usepackage{times}
\usepackage{setspace}
\singlespacing
\usepackage{amsmath,amssymb, amsthm}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[hang, flushmargin]{footmisc}
\usepackage[colorlinks=true]{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{footnotebackref}
\usepackage{url}
\usepackage{listings}
\usepackage[most]{tcolorbox}
\usepackage{inconsolata}
\usepackage[papersize={8.5in,11in}, margin=1in]{geometry}
\usepackage{float}
\usepackage{caption}
\usepackage{esint}
\usepackage{url}
\usepackage{enumitem}
\usepackage{subfig}
\usepackage{wasysym}
\newcommand{\ilcode}{\texttt}
\newcommand{\p}{\partial}
\newcommand{\vphi}{\varphi}
\usepackage{etoolbox}
\usepackage{physics}
\usepackage{xcolor}
\usepackage{subfiles}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

\begin{document}

\title{\textbf{CSDS 440 Class Project: \\Adversarial Machine Learning}}

\author{Shaochen (Henry) Zhong, \ilcode{sxz517} \\ Minyang Tie, \ilcode{mxt497} \\ Alex Useloff, \ilcode{adu3} \\ Austin Keppers, \ilcode{agk51} \\ David Meshnick, \ilcode{dcm101}\\}
\date{Due and submitted on 12/04/2020 \\ Fall 2020, Dr. Ray}
\maketitle

\section{Introduction}

\section{Shaochen (Henry) Zhong Individual Report}

\section{Minyang Tie Individual Report}

\section{Alex Useloff Individual Report}

\section{Austin Keppers Individual Report}
\subfile{individual_reports/agk51}

\section{David Meshnick Individual Report}

\section{Algorithm Comparison}

\end{document}

### 2020-12-04 report/individual_reports/agk51.tex
🎉 Add basic setup with Austin's subfile.

\documentclass[../article.tex]{subfiles}

\begin{document}

The main algorithm that I focused on for this report was Defensive Distillation.
Defensive distillation is a way to train a deep neural network classifier with the goal of better defending against
adversarial examples that was first proposed in the paper \emph{Distillation as a Defense to Adversarial Perturbations against Deep Neural Networks} by Papernot et all.
The main idea behind Defensive distillation is that Deep Neural Networks are susceptible to adversarial examples because they make overly confident predictions when a sample has elements of two different classes.
Defensive Distillation attempts to deal with this by using a classifier that is trained on soft labels instead of hard labels. Soft labels provide probabilities that an example belongs to each of the classes in a model rather than identifying a specific lass the example belongs to.

Distillation is a technique that was created in order to run Deep Neural Networks on devices with lower computational power by reducing the size of the network. The idea is that hard labels can be used to train a large neural network, and then this classifier can be used to create soft labels to train a smaller neural network with the goal of obtaining an accuracy similar to the original larger classifier. Defensive distillation uses a variation of this technique in order to create a deep neural network that can better classify adversarial examples.

 The output of the neural network used in distillation must be a Softmax layer with a temperature parameter. The output of a softmax layer is as follows

\[ F(X) = \left[\frac{e^{z_i(X) / T}}{\sum_{l=0}^{N-1}e^{z_l(X) / T}}\right]_{i \in 0 \dots N - 1} \]

where $Z(X)$ is the output of the previous layer and $F(X)$ is an output that corresponds to a vector with a probability for each class. The temperature value $T$ in the Softmax layer determines how confident the classifier will be about the most probable class. A high temperature value will cause the different class probabilities to be closer together whereas a low temperature will cause the most probable classes to have  a probability further apart from the less probable classes. This is because the exponent is divided by the temperature and reducing the exponents value by the same amount for all classes will cause the output values to be closer to each other

In Defensive Distillation a neural network where the last layer is a softmax layer is trained using a dataset with hard labels. The temperature of the Softmax layer is set to a high value (something greater than 1) so that the classifier will output values with larger values for each class. This means that the output will emphasis ambiguities in certain examples that may have similarities to a different class. The examples are then passed through the trained neural network at the same high temperature and the output of the classifier is recorded as a soft label for that example. Whereas in distillation a smaller model is trained using the soft labels, in defensive distillation the goal is a classifier more resilient against adversarial examples rather than a performant one so the second classifier is of the same size as the first one. When this second classifier is trained using the soft labels it the temperature of the Softmax label is set to a high value. When it is then being tested the Temperature is lowered to 1 so that the classifier outputs more confident probabilities.

Theoretical justifications presented in the paper as to why defensive distillation works against adversarial examples include that a higher temperature reduces the model's sensitivity to small perturbations in the input to the classifier, and that defensive distillation improves the generizability of the classifier outside of the training sample.

The researchers were able to use defensive distillation to lower the success rate of adversarial examples from 95.89\% to 0.45\% on the MNIST dataset and from 87.89\% to 5.11\% on the CIFAR10 dataset. The distillation did result in a moderate decrease in the accuracy on non-adversarial examples with a 1.28\% decrease on the MNIST dataset and a 1.37\% decrease on the CFAIR10 dataset. The models performed better against adversarial examples at higher distillation temperatures with the temperature of 100 (the highest that they tested) performing the best. They also show that defensive distillation increases the robustness of the classifier produced.

The second paper I read finds a way to revert adversarial examples into non-adversarial examples before feeding them into a classifier instead of training the classifier to handle adversarial images. This paper was \emph{Defense-GAN: Protecting Classifiers Against Adversarial Attacks Using Generative Models} by Samangouei et all. and its idea is to use Generative Adversarial Networks to help protect Deep Neural Networks against adversarial examples.

Generative Adversarial Networks consist of two networks: $D$ and $G$. $D$ is a binary classifier for examples $x$, and $G$ learns how to craft examples with the dimensionality of $x$ from a random vector $z$. $G$ learns to map $z$ to $G(z)$ similar to $x$ and $D$ then learns how to distinguish between $x$ and $G(z)$. In the paper generative networks were trained with a loss function based on Wasserstein distance which is as follows:

\[ \min_G \max_D V_w(D, G) = \mathbf{E}_{x \sim p_data(x)}[D(x)] -  \mathbf{E}_{x \sim p_z}[D(G(z))]\]

Feeding non-adversarial examples through the generative network should barely effect the examples so long as $p_g$ converges to $p_{data}$. This means that legitimate example will not be altered by being fed through the network while adversarial example will be altered.

Defense-GAN works by finding an input $z^*$ to the GAN that will match the original input $x$ as closely as possible. $G(z^*)$ is what will then actually be fed into the classifier. The exact expression to be minimized is

\[ \min_z \|G(z) - x\|^2_2\]

Gradient descent is then run on this function with random restarts to find $z^*$

The reason this approach is useful is because it assumes very little about the type of attack or the classifier that is being used. The classifier used to classify the images can also be trained using either the original training set or images generated by the generative network.

The researchers tested different combinations of attacks and defenses on the MNIST dataset as well as the Fashion-MNIST data set. The types of attacks included both black box and white box attacks. Defense-GAN performed well on the MNIST data set on many different types of attacks and classifiers, while other types of defenses tested performed well against only certain types of attacks. The performance from training the classifier on the original images and the images from the Generative Adversarial Network were both comparable. Increasing the number of random restarts increased the classification accuracy. The number of iterations of gradient descent generally increased the accuracy but against adversarial examples high numbers of iterations eventually decreased the accuracy.

Defense-GAN can also be used to detect the use of adversarial examples. This is because examples with larger perturbations from the original examples will be further away from the image produced by the generative network than unchanged images. Thus the authors propose used the mean squared error of the original image and the image output by the GAN to detect attacks.

Two difficulties the authors note that may need to be considered when deploying defense-GAN are the training of adversarial networks as well as the choice of parameters. They note that there are still challenges in training GANs and the choices of $L$, the number of gradient descent iterations, and $R$, the number of random restarts, are both important factors in the effectiveness of defense-GAN.

\end{document}

### 2020-12-04 algos/defence/detector.py
✨ Add Minyang's finalized defense algos.

@@ -1,0 +1,34 @@
+
+import keras
+import numpy as np
+
+def build_detector(model):
+    layers = [layer for layer in model.layers]
+    num_layers = len(layers)
+    output = keras.layers.Dense(2)(layers[num_layers-2].output)
+    detector = keras.Model(inputs=layers[0].input, outputs=output)
+    # detector.summary()
+    return detector
+
+def train(model, x_train, x_train_adv):
+    nb_train = x_train.shape[0]
+    x_train_detector = np.concatenate((x_train, x_train_adv), axis=0)
+    y_train_detector = np.concatenate((np.array([[1,0]]*nb_train), np.array([[0,1]]*nb_train)), axis=0)
+
+    model.compile(optimizer='rmsprop',loss='binary_crossentropy',metrics=['accuracy'])
+    model.fit(x_train_detector, y_train_detector, epochs=20, batch_size=32)
+    return 0
+
+def result(model, x_test, x_test_adv, total_size):
+    flag_adv = np.sum(np.argmax(model.predict(x_test_adv), axis=1) == 1)
+
+    print(f"Adversarial test data (first {total_size} images):")
+    print("Flagged: {}".format(flag_adv))
+    print("Not flagged: {}".format(total_size - flag_adv))
+
+    flag_original = np.sum(np.argmax(model.predict(x_test[:total_size]), axis=1) == 1)
+
+    print(f"Original test data (first {total_size} images):")
+    print("Flagged: {}".format(flag_original))
+    print("Not flagged: {}".format(total_size - flag_original))
+    return 0

### 2020-12-04 demos/fgsm_quick_test.py
✨ 🔨 Add and update finalized quick test and eval arena files.

@@ -20,11 +20,23 @@ tf.compat.v1.logging.set_verbosity(tf.compat.v1.logging.ERROR)
 
 print(tf.__version__)
 
-(x_train, y_train), (x_test, y_test), min_, max_ = load_dataset('mnist')
+# (x_train, y_train), (x_test, y_test), min_, max_ = load_dataset('mnist')
+# path = get_file('mnist_cnn_original.h5', extract=False, path=ART_DATA_PATH,
+#                 url='https://www.dropbox.com/s/p2nyzne9chcerid/mnist_cnn_original.h5?dl=1')
+# classifier_model = load_model(path)
 
-path = get_file('mnist_cnn_original.h5', extract=False, path=ART_DATA_PATH,
-                url='https://www.dropbox.com/s/p2nyzne9chcerid/mnist_cnn_original.h5?dl=1')
+
+# (x_train, y_train), (x_test, y_test), min_, max_ = load_dataset('mnist')
+# path = get_file('mnist_cnn_original.h5', extract=False, path=ART_DATA_PATH,
+#                 url='https://www.dropbox.com/s/p2nyzne9chcerid/mnist_cnn_original.h5?dl=1')
+# classifier_model = load_model(path)
+
+(x_train, y_train), (x_test, y_test), min_, max_ = load_dataset('cifar10')
+path = get_file('cifar_resnet.h5',extract=False, path=ART_DATA_PATH,
+                url='https://www.dropbox.com/s/ta75pl4krya5djj/cifar_resnet.h5?dl=1')
 classifier_model = load_model(path)
+
+
 classifier = KerasClassifier(clip_values=(min_, max_), model=classifier_model, use_logits=False)
 
 num = 100
@@ -52,7 +64,7 @@ print("Incorrectly classified: {}".format(num-nb_correct_pred))
 
 # x_0_arr = np.array([x_test[0] * num])
 # attacker = FastGradientMethod(classifier, eps=0.1)
-attacker = FastGradientSignMethod(classifier, eps=10, batch_size = 8)
+attacker = FastGradientSignMethod(classifier, eps=0.5, batch_size = 8)
 # x_test_adv = attacker.generate(x_test[:num]) # non-targeted
 # x_test_adv = attacker.generate_targeted(x_test[:num], x_test[0]) #targeted
 # x_test_adv = attacker.generate_iterative(x_test[:num]) #iterative non-targeted

### 2020-12-04 demos/hsj_quick_test.py

@@ -18,12 +18,16 @@ warnings.filterwarnings('ignore')
 
 
 
-(x_train, y_train), (x_test, y_test), min_, max_ = load_dataset('mnist')
+# (x_train, y_train), (x_test, y_test), min_, max_ = load_dataset('mnist')
+# path = get_file('mnist_cnn_original.h5', extract=False, path=ART_DATA_PATH,
+#                 url='https://www.dropbox.com/s/p2nyzne9chcerid/mnist_cnn_original.h5?dl=1')
+# classifier_model = load_model(path)
 
-
-path = get_file('mnist_cnn_original.h5', extract=False, path=ART_DATA_PATH,
-                url='https://www.dropbox.com/s/p2nyzne9chcerid/mnist_cnn_original.h5?dl=1')
+(x_train, y_train), (x_test, y_test), min_, max_ = load_dataset('cifar10')
+path = get_file('cifar_resnet.h5',extract=False, path=ART_DATA_PATH,
+                url='https://www.dropbox.com/s/ta75pl4krya5djj/cifar_resnet.h5?dl=1')
 classifier_model = load_model(path)
+
 classifier = KerasClassifier(clip_values=(min_, max_), model=classifier_model, use_logits=False)
 
 num = 100

### 2020-12-04 algos/fast_gradient_sign_method.py
🚚 Migrate Henry's attack algos to algos/attack/ dir.

@@ -1,271 +1,0 @@
-# MIT License
-#
-# Copyright (C) The Adversarial Robustness Toolbox (ART) Authors 2018
-#
-# Permission is hereby granted, free of charge, to any person obtaining a copy of this software and associated
-# documentation files (the "Software"), to deal in the Software without restriction, including without limitation the
-# rights to use, copy, modify, merge, publish, distribute, sublicense, and/or sell copies of the Software, and to permit
-# persons to whom the Software is furnished to do so, subject to the following conditions:
-#
-# The above copyright notice and this permission notice shall be included in all copies or substantial portions of the
-# Software.
-#
-# THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE
-# WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
-# AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT,
-# TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
-# SOFTWARE.
-
-from __future__ import absolute_import, division, print_function, unicode_literals
-
-import logging
-from typing import Optional, Union, TYPE_CHECKING
-
-import numpy as np
-
-from art.config import ART_NUMPY_DTYPE
-from art.attacks.attack import EvasionAttack
-from art.estimators.estimator import BaseEstimator, LossGradientsMixin
-from art.estimators.classification.classifier import ClassifierMixin
-from art.utils import (
-    compute_success,
-    get_labels_np_array,
-    random_sphere,
-    projection,
-    check_and_transform_label_format,
-)
-
-if TYPE_CHECKING:
-    from art.utils import CLASSIFIER_LOSS_GRADIENTS_TYPE
-
-logger = logging.getLogger(__name__)
-
-
-class FastGradientSignMethod(EvasionAttack):
-    """
-    This attack was originally implemented by Goodfellow et al. (2015) with the infinity norm (and is known as the "Fast
-    Gradient Sign Method"). Developers of ART implemented Goodfellow method by extending its attack to other norms.
-
[…]

### 2020-12-04 algos/hop_skip_jump.py

@@ -1,322 +1,0 @@
-# MIT License
-#
-# Copyright (C) The Adversarial Robustness Toolbox (ART) Authors 2019
-#
-# Permission is hereby granted, free of charge, to any person obtaining a copy of this software and associated
-# documentation files (the "Software"), to deal in the Software without restriction, including without limitation the
-# rights to use, copy, modify, merge, publish, distribute, sublicense, and/or sell copies of the Software, and to permit
-# persons to whom the Software is furnished to do so, subject to the following conditions:
-#
-# The above copyright notice and this permission notice shall be included in all copies or substantial portions of the
-# Software.
-#
-# THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE
-# WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
-# AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT,
-# TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
-# SOFTWARE.
-"""
-Base on ART's infra and _compute_update() structure, a parial implementation of the HopSkipJump attack from Jianbo et al. (2019).
-| Paper link: https://arxiv.org/abs/1904.02144
-"""
-# assume norm = np.inf and target = false
-
-from __future__ import absolute_import, division, print_function, unicode_literals
-
-import logging
-from typing import Optional, Tuple, Union, TYPE_CHECKING
-
-import numpy as np
-from tqdm import tqdm
-
-from art.config import ART_NUMPY_DTYPE
-from art.attacks.attack import EvasionAttack
-from art.estimators.estimator import BaseEstimator
-from art.estimators.classification import ClassifierMixin
-from art.utils import compute_success, to_categorical, check_and_transform_label_format
-
-if TYPE_CHECKING:
-    from art.utils import CLASSIFIER_TYPE
-
-logger = logging.getLogger(__name__)
-
-
-class HopSkipJump(EvasionAttack):
-
-
-    attack_params = EvasionAttack.attack_params + [
[…]

### 2020-12-04 report/code/util.py
⚙️ Add code to calculate 95% CI.

@@ -1,0 +1,30 @@
+import math
+
+def ci95(acc_1, acc_2, size):
+    f = acc_1 - acc_2
+    v = acc_1* (1- acc_1)/size + acc_2*(1-acc_2)/size
+    std = math.sqrt(v)
+    coe = 1.96
+    bound_1 = f + coe * std
+    bound_2 = f - coe * std
+    result = [bound_1, bound_2]
+    result.sort()
+    # print(v)
+    result = tuple(result)
+    print(f'{f} +- {coe} * {std} = {result}')
+
+
+# ci95(0.123, 0.0829, 10000)
+# ci95(0.10, 0.098, 10000)
+# ci95(0.0829, 0.0041, 10000)
+
+
+
+ci95(0.912, 0.904, 500)
+ci95(0.904, 0.618, 500)
+
+ci95(0.012, 0.004, 500)
+ci95(0.28, 0.012, 500)
+
+
+

### 2020-12-04 report/article.tex
✨ Add basic framework and content for comparative study.

@@
 \usepackage{wasysym}
-\newcommand{\ilcode}{\texttt}
+\newcommand{\ilc}{\texttt}
 \newcommand{\p}{\partial}
@@
 
-\makeatletter
-\renewcommand{\@seccntformat}[1]{}
-\makeatother
+% \makeatletter
+% \renewcommand{\@seccntformat}[1]{}
+% \makeatother
 
@@
 
-\author{Shaochen (Henry) Zhong, \ilcode{sxz517} \\ Minyang Tie, \ilcode{mxt497} \\ Alex Useloff, \ilcode{adu3} \\ Austin Keppers, \ilcode{agk51} \\ David Meshnick, \ilcode{dcm101}\\}
+\author{Shaochen (Henry) Zhong, \ilc{sxz517} \\ Minyang Tie, \ilc{mxt497} \\ Alex Useloff, \ilc{adu3} \\ Austin Keppers, \ilc{agk51} \\ David Meshnick, \ilc{dcm101}\\}
 \date{Due and submitted on 12/04/2020 \\ Fall 2020, Dr. Ray}
@@
 
-\section{Introduction}
+\renewcommand{\abstractname}{Contributions}
+\begin{abstract}
+We as a group of five have looked into the field of adversarial machine learning and specifically investigated several algorithms regarding aspects of attack (evasion, poisoning) and defense (detector, transformer, pre-process).
+Inside the group, overall contribution are as following:
+\begin{itemize}
+    \item Henry:
+    \begin{itemize}
+        \item Read 3 papers on algorithms.
+        \item Implemented 2 algorithms (\ilc{FGSM} and \ilc{Hop Skip Jump}) with 3 extensions.
+        \item Piplined attack algorithms to work with 2 datasets, collected almost all (7 algorithms/useable extensions) attack experiments data (except \ilc{backdoor} and \ilc{one pixel attack}) for the comparative evaluations.
+        \item Piplined and collected experiments data for \ilc{FGSM, Hop Skip Jump, DeepFool} attacks (and their useable extensions) against \ilc{Detector} and \ilc{Spatial Smoothing} defenses on 2 datasets.
+        \item Implemented $L_2$ and $L_{\infty}$ \textit{perturbation budget} to aid comparative evaluation.
+        \item Wrote \textbf{Introduction and Significance} section.
+        \item Plotted all graphs and charts in \textbf{Comparative Study and Discussion}.
+        \item Helped group move forward by making technical decisions, distributing works, setting up deadlines, and facilitating coordination between groupmates.
+    \end{itemize}
+    \item Minyang:
+    \item Alex:
+    \item Austin:
+    \item David:
+\end{itemize}
+\end{abstract}
 
-\section{Shaochen (Henry) Zhong Individual Report}
+\setcounter{tocdepth}{4}
+\vspace{0.5cm}
+{\hypersetup{hidelinks}
+\tableofcontents
+}
 
-\section{Minyang Tie Individual Report}
+\newpage
 
-\section{Alex Useloff Individual Report}
+\section{Introduction and Significance}
 
-\section{Austin Keppers Individual Report}
+\section{Individual Reports}
+
+\subsection{Shaochen (Henry) Zhong's Individual Report}
+\subsubsection{Overview}
+
+\subsubsection{\ilc{Fast Gradient Sign Method}}
+\paragraph{Algorithm Intuition}
+\paragraph{Algorithm Implementation}
+\paragraph{Experiments}
+\paragraph{Evaluation}
+
+\subsubsection{\ilc{Hop Skip Jump}}
+\paragraph{Algorithm Intuition}
+\paragraph{Algorithm Implementation}
+\paragraph{Experiments}
+\paragraph{Evaluation}
+
+\subsubsection{\ilc{Feature Collision}}
+\paragraph{Algorithm Intuition}
+
+\subsection{Minyang Tie's Individual Report}
+
+\subsection{Alex Useloff's Individual Report}
+
+\subsection{Austin Keppers' Individual Report}
 \subfile{individual_reports/agk51}
 
-\section{David Meshnick Individual Report}
+\subsection{David Meshnick's Individual Report}
 
-\section{Algorithm Comparison}
+\section{Comparative Study and Discussion}
+
+In this section, we will present a comparative study between some algorithms (and their comparable extensions) we implemented.
+
+\subsection{Overview}
+
+\subsubsection{Datasets and Sample Selections}
+
+For the tesing datasets, we opted to use \textit{MINIST} \cite{cite:minist} and \textit{CIFAR-10} \cite{cite:cifar10}.
+In short, \textit{MINIST} is a database of handwritten digits and \textit{CIFAR-10} is a database for tiny images, as demonstrated below in  [\figurename{\ \ref{MINIST}}] and [\figurename{\ \ref{CIFAR}}].
+
+\begin{figure}[H]
+\minipage{0.4\textwidth}
+    \centering
+    \includegraphics[width = \textwidth]{{fig/MINIST.png}}
+    \caption{An selection of \textit{MINIST} database}
+    \label{MINIST}
+\endminipage\hfill
+\minipage{0.4\textwidth}
+    \centering
+    \includegraphics[width =\textwidth]{{fig/CIFAR10.png}}
+    \caption{An selection of \textit{CIFAR-10} database}
+    \label{CIFAR}
+\endminipage
+\end{figure}
+
+\noindent Our decision of using these two datasets are base on the consideration of:
+\begin{itemize}
+    \item Both datasets are pre-labeled and have pretrained model available for use. So we may save time on training the victim model(s), and also have some consistent baselines to refer to.
+    \item Both datasets are lightweight in terms of image resolutions, so when evaluating computational-heavy algorithms (e.g.
+\ilc{Hope Skip Jump}), we are able to get the experiments data either locally or with minimum use of cloud services.
+    \item Having ORC and image classifying tasks (in general) together can be a very fair coverage of the actual applications of adversarial learning.
+    \item \textit{MINIST} specifically has a close-to-pure background color, which is a great for human to evaluate as sometime the perturbation on a colorful picture can be unnoticeable to human eyes.
+    \item The toolbox of choice \textit{adversarial-robustness-toolbox} a.k.a \ilc{ART} have wrapper methods around these two models, and can load their pretained models as \ilc{ART}'s victim classifiers (we have specifically inquired Dr.
+Ray that it is ok to \ilc{import} this kind of facilities).
+\end{itemize}
+
+We have thought about using a third database like \textit{ImageNet} or \textit{IRIS}, but with the combinations of attacks and defenses algorithms we already have a very heavy experiments workload.
+So we opted to only use these two.
+However, considered the image quality of \textit{MINIST} and \textit{CIFAR-10} are rather on the low side, we used some \textit{ImageNet} images to demo our work and concepts.
+
+\subsubsection{ART}
+
+\textit{adversarial-robustness-toolbox}\cite{cite:art} a.k.a \ilc{ART} is an IBM-sponsered library that provides tools for necessary adversarial learning experiments.
+We have utlized \ilc{ART}'s facilities on loading dataset, wrapping victim classifiers, and piplining attack and defense algorithms together.
+We cannot finish this project without this library, so much credit to them.
+
+\subsubsection{Metrics}
+
+As we are not doing binary classifications, \textit{accuracy} will be our top piority.
+This is also the case for general goal of adversarial learning, as we either what to attack the model to lower its \textit{accuracy}, or we want to defend from an attack with increased robustness -- thus higher  \textit{accuracy}.\newline
+
+\noindent However, another important aspect of adversarial learning is, in most of the cases, we want the our attack image to be only ``adversarial'' to a computer model, but not to human eyes.
+This is first because without such restraint we may simply swap a dog picture with a cat picture and call it a successful attack, which will make the task meaningless.
+Second, it is because for most of the time we want our attack to be ``stealthy'' -- and a collection of pixels noises is simply not so much of that.
+
+\begin{figure}[H]
+\minipage{0.25\textwidth}
+    \includegraphics[width = \textwidth]{{fig/google_fgsm_1.png}}
+\endminipage\hfill
+\minipage{0.25\textwidth}
+    \includegraphics[width = \textwidth]{{fig/google_fgsm_2.png}}
+\endminipage\hfill
+\minipage{0.25\textwidth}
+    \includegraphics[width = \textwidth]{{fig/google_fgsm_3.png}}
+\endminipage\hfill
+\minipage{0.25\textwidth}
+    \includegraphics[width = \textwidth]{{fig/google_fgsm_4.png}}
+\endminipage
+\caption{A Labrador Retriver with different levels of perturbations}
+\label{fgsm_dog}
+\end{figure}
+
+Thus, keeping the ``semantic'' of the original image is important in terms of making adversarial examples.
+However we must have a way to quantify such perturbations -- as it can be very hard to tell like shown in [\figurename{\ \ref{fgsm_dog}}] \cite{cite:google_fgsm} -- so that we can numerically conclude and justify the claim if a image has lost it semantic (and by how much).
+
+The metrics we found is \textit{perturbation budget}\cite{cite:perb_budget}, it defined as:
+
+\begin{equation}
+     \epsilon = || x_{\text{adv}} - x ||
+     \label{perb_budget_equation}
+\end{equation}
+
+where $epsilon$ in [Equation \ \ref{perb_budget_equation}] is the \textit{perturbation budget}.
+However, we have different choices on calculating the distance metrics.
+In this case, we opted to use $L_2$ and $L_{\infty}$ as they represent the \textsc{Euclid} distance and maximum magnitude between pixels -- which covered the perturbation of a picture both holistically and ``extremely.''
+
+Specifically in practice, we calcualte the $L_2$ and $L_{\infty}$ of two images channel by channel then add them together.
+The principle is we will want the these numbers to be as small as possible, as long as the adversarial image we created still have an adversarial affect to a model.
+Note if an algorithm is iterative, a smaller \textit{perturbation budget} also means smaller computation cost -- as less iteration were done.\newline
+
+\noindent Another thing that maybe worth mentioning is since we used pretained victim model, we didn't do anything like N-fold cross validation as we are seeking effects out of a trained model, but not to train one (maybe except \ilc{Neural Cleanse} as it does retain the model).
+But we do average our trials to make sure our experiment results are reproducable.
+
+\subsubsection{Adversarial Rivalry}
+
+We have implemented and experimented multiple attack and defense algorithms, but not all of them can be compared together due to various reasons.
+In our cases, we opted to not to have some algorithms compared together, or even not to include some algorithm in our comparative study.
+
+We opted to compare \ilc{Fast Gradient Sign Method} (non-targeted, with one-shot and iterative implementions), \ilc{Hop Skip Jump}, \ilc{DeepFool} (and \ilc{Dynamic DeepFool} -- an extension implemented by David) together as they are all the non-targed evasion algorithm we implemented.
+We opted to not include \ilc{Backdoor} in this set of comparsion as it evasion attacks were done in the assumption of having a trained model, it doesn't make sense to have posioning -- which can alter the training set of a model -- to be part of the comparsion.
+Similarily, the two targeted extensions \ilc{FGSM} is excluded from this comparsion as in this context it is the magnitude of decrease of model \textit{accuracy} in general we care about, but not which exact label the model most classifies to.
+
+Likewise, we opted to not compare any other algorithm except \ilc{Backdoor} to against \ilc{Neural Cleanse}, as: Minyang please input here.
+
+Also we are not comparing different defense algorithms against a same attack algorithm.
+This is not because we are not interested in the performance difference between defense algorithm.
+It is simply because we have already elimited \ilc{Neural Cleanse} due to its retrain nature; and for the other two remained defense algorithm \ilc{Binary Input Detector} and \ilc{Spatial Smoothing}, the former one is designed to recognize and flag an adversarial image, where the latter is to increase model robustness so that it can better classified adversarially perturbed images -- so they can't be compared.
+
+\subsection{Attack Algorithms}\label{attack_algo}
+
+Note \ilc{I-FGSM} represents (non-targted, one-shot) \ilc{Iterative Fast Gradient Sign Method};  \ilc{D-DeepFool} represents \ilc{Dynamic DeepFool}.
+The \ilc{FGSM} is running with params being \ilc{batch\_size = 32, eps = 3}, and the \ilc{I-FGSM} is running on the same setting with \ilc{eps\_step = 0.05} as we have found in Henry's individual report with \ilc{eps\_step > 0.05} we might ``overshot'' ourself.
+\newline
+
+\ilc{Hop Skip Jump} a.k.a.
+\ilc{HSJ} is a very computational-heavy algorithm.
+When possible, we will use \ilc{max\_iter=64, max\_eval=1000, init\_eval=100} which is close to the authors suggested setting (except the authors suggests \ilc{max\_eval = 100000} which is impossible to replicate with our resource).
+But often time we are limited for \ilc{max\_iter=8, max\_eval=100, init\_eval=10}.
+\newline
+
+Unless specifically addressed, the base line model is a the pretrained model of dataset wrapped in \ilc{ART}'s \ilc{KerasClassifier}.
+
+\subsubsection{Evasion}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.8\textwidth]{{fig/attack_minist_acc.png}}
+    \caption{Accuracy comparsion of evasion attack algorithms on \textit{MINIST}}
+    \label{attack_minist_acc}
+\end{figure}
+
+By observating  [\figurename{\ \ref{attack_minist_acc}}] it can be clearly tell that the presented algorithms are in three different ``levels.'' With \ilc{HSJ} showing the best performance and \ilc{DeepFool} and \ilc{D-DeepFool} showing identical performance, the only interesting question left is if \ilc{FGSM} is significantly different from \ilc{I-FGSM}.
+
+We then try to find the $95 \%$ CI of $E_{\ilc{FGSM}} - E_{\ilc{I-FGSM}}$ with a null hypothesis of they have no difference. Note the sample size of tested \textit{MINIST} is $10000$.
+
+\begin{align*}
+    F &= 0.299 - 0.2881 \\
+    &= 0.0109 \\
+    V(F) &= 0.299(1-0.299)/10000 + 0.2881(1-0.2881)/10000 \\
+    &= 0.000041469739\\
+    \Rightarrow \sigma &= 0.006439700226 \\
+    95 \% \text{CI} &= 0.0109 \pm 1.96 \cdot 0.006439700226 = (-0.001721812443, 0.02352181244)
+\end{align*}
+
+With $0$ lies in the $95 \%$ CI, we can't reject the null hypothesis and \ilc{FGSM} and \ilc{I-FGSM} are not different in terms of accuracy performance in this experiment.
+This is consistent to our understanding of the algorithms as \ilc{I-FGSM} is suppose to be the iterative version of \ilc{FGSM}, it performed slightly ``better'' in number on \textit{adversarial acc} probably just because the adversarial image is generated closer to the decision boundaries of the model and therefore a bit more ``confusing'' -- we will analysize this issue closer with the following budget graph [\figurename{\ \ref{attack_minist_budget}}].
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.8\textwidth]{{fig/attack_minist_budget.png}}
+    \caption{Budget comparsion of evasion attack algorithms on \textit{MINIST}}
+    \label{attack_minist_budget}
+\end{figure}
+
+By investigating the [\figurename{\ \ref{attack_minist_budget}}] we may confirm our thinking that \ilc{I-FGSM} generated adversarial examples are less aggressive (and thus closer to the decision boundaries), as it has a lower mean $L_2$ and mean $L_\infty$ (we can't do $95 \%$ CI on this as the sample size has no bearing to the perturbation budget).\newline
+
+In our pervious observation on [\figurename{\ \ref{attack_minist_acc}}] we said \ilc{HSJ} has the best performance in terms \textit{adversarial acc}.
+Now we know that \ilc{HSJ} did such with minimum perturbation budget spent (by having the lowrest mean $L_2$ and mean $L_\infty$ across the board).
+However, the cost of doing this is very high, the runtime of \ilc{HSJ} is close $100$ times of other algorithm.
+These observations are also consistent to our understanding of \ilc{HSJ}, as it is doing \textit{binary search} until it crosses the decision boundary -- so it can perserve a high amount semantic from the original image, at the cost of spending a lot of time to find such image.\newline
+
+David please explain a bit on DeepFool as why it perturbed a huge amount while performed not so well, and maybe also why its $L_\infty$ is a lot higher than $L_2$.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.8\textwidth]{{fig/attack_cifar10_acc.png}}
+    \caption{Accuracy comparsion of evasion attack algorithms on \textit{CIFAR-10}}
+    \label{attack_cifar10_acc}
+\end{figure}
+
+We then repeated the same experiment on $100000$ \textit{CIFAR-10} examples and got the result of [\figurename{\ \ref{attack_cifar10_acc}}].
+This time we have a different outcome between \ilc{DeepFool} and \ilc{D-DeepFool}, so we will analysis $E_{\ilc{FGSM}} - E_{\ilc{I-FGSM}}$, $E_{\ilc{DeepFool}} - E_{\ilc{D-DeepFool}}$, and $E_{\ilc{I-FGSM}} - E_{\ilc{HSJ}}$ (as they are closer this time).
+With an aid of a script and a null hypothesis of having no difference, we have:
+
+\begin{itemize}
+    \item  $95 \%$ CI of $E_{\ilc{FGSM}} - E_{\ilc{I-FGSM}}$: \ilc{(0.031694853818380074, 0.04850514618161992)}, rejected.
+    \item  $95 \%$ CI of $E_{\ilc{DeepFool}} - E_{\ilc{D-DeepFool}}$: \ilc{(-0.006278442326911505, 0.010278442326911509)}, cannot rejected.
+    \item  $95 \%$ CI of $E_{\ilc{I-FGSM}} - E_{\ilc{HSJ}}$: \ilc{(0.07325244583218875, 0.08434755416781124)}, rejected.
+\end{itemize}
+
+It is a bit suprisized to see the null hypothesis of $E_{\ilc{FGSM}} - E_{\ilc{I-FGSM}} = 0$ can be rejected.
+This is probably because \textit{CIFAR-10} has more label catagories where \textit{MINIST} only has 10 digits, thus decision boundaries between (more) different labels to be closer.
+The observation of having an overall lower \textit{benign acc} also confirms this assumption.
+We will look into it again in the following budget analysis [\figurename{\ \ref{attack_cifar10_budget}}].
+
+Also, with $E_{\ilc{I-FGSM}} - E_{\ilc{HSJ}} = 0$ rejected, we may say that \ilc{HSJ} indeed performs better than \ilc{I-FGSM}.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.8\textwidth]{{fig/attack_cifar10_budget.png}}
+    \caption{Budget comparsion of evasion attack algorithms on \textit{CIFAR-10}}
+    \label{attack_cifar10_budget}
+\end{figure}
+
+The budget analysis [\figurename{\ \ref{attack_cifar10_budget}}] comfirms our thinking as the perturbation budgets are larger acrossed the board in comparision to \textit{MINIST}.
+Also all other observation made from the \textit{MINIST} budget graph [\figurename{\ \ref{attack_minist_budget}}] are also true in this \textit{CIFAR-10} budget graph.
+
+\subsubsection{Poisoning}
+Please refer to Section \ref{defense_transformer} as we have only one poisoning attack algorithm and want to analysize it in combination with its designated defense: \ilc{Neural Cleanse}.
+
+\subsubsection{Conclusion}
+
+We have made the obersvation of \ilc{HSJ} is having the best \textit{accuracy} performance.
+With \ilc{HSJ} and \ilc{I-FGSM} being more successful on controlling their perturbation budget -- due to their iterative nature -- and therefore probably are overall more reliable attacks as they can generate more effective (i.e.
+more confuse to a modal) adversarial examples while preserve better semanic of the original benign image (i.e.
+the pertubation is less obvious to human's eyes).
+
+Note we also discovered \ilc{I-FGSM} and \ilc{HSJ} are computationally-heavy (especially the latter), due to their iterative nature and the need of many binary search operations in the case of \ilc{HSJ}.
+So it is suspected this sort of attacks can be better prevented by implementing flow control mechanism of the model \ilc{predict()} API -- as without enough steps of iterations, these two algorithms won't easily find the decision boundary of the model.\newline
+
+\ilc{DeepFool} and \ilc{D-DeepFool} have shown very similar performance across this section of experiments and their performance are considerably lacking both in terms of \textit{adversarial acc} and \textit{perturbation budget}.
+David, please again summarize a bit here.
+
+\subsection{Defense Algorithms}
+
+The setup of algorithms and environment remain consistent to Section \ref{attack_algo}, with the exception of we ran \ilc{HSJ} with the params of \ilc{max\_iter=8, max\_eval=100, init\_eval=10} due to resource concern.\newline
+
+\noindent Unless specifically addressed, the base line model is a the pretrained model of dataset wrapped in \ilc{ART}'s \ilc{KerasClassifier}; and the testing sample size of datasets are $500$ (per each databset).
+
+\subsubsection{Detector}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.8\textwidth]{{fig/bd_minist_acc.png}}
+    \caption{Effectiveness comparision of evasion attack algorithms v. \ilc{Binary Input Detector} on \textit{MINIST}}
+    \label{bd_minist_acc}
+\end{figure}
+
+\ilc{Binary Input Detector} a.k.a \ilc{BID} is algorithm that detects and flags adversarial examples out of a dataset.
+Since the workflow of our experiment is to get the \textit{benign acc} with original benign examples, then make them into adversarial exmaples to get the \textit{adversarial acc}, then we ask \ilc{BID} to run on both the benign example set and the adversarial example set.
+
+In the adversarial example set, \ilc{BID} should aim for a $100 \%$ as every input example of the set is adversarial; vice versa, \ilc{BID} should aim for a $0 \%$ in the benign example set as none of the input exmaple are adversarial -- we times this benign flagging percentage with an $-1$ do show that it is a negative impact.\newline
+
+\noindent First, we may tell there is much difference on \textit{adversarial flag} except for \ilc{D-DeepFool}, as we have $95 \%$ of $E_{\ilc{HSJ}} - E_{\ilc{FGSM}}$ (the biggest difference on \textit{adversarial flag} excluding \ilc{D-DeepFool}) to be \ilc{(-0.027824596689983806, 0.04382459668998382)}, so we cannot reject the null hypothesis of \ilc{FGSM, I-FGSM, HSJ, DeepFool} having no significant difference on \textit{adversarial flag}.\newline
+
+Thus, the interest is left to \textit{benign flag}, we cannot rejected $E_{\ilc{FGSM}} - E_{\ilc{I-FGSM}} = 0$ by having a  $95 \%$ of \ilc{(-0.0030318578671047047, 0.019031857867104707)}.
+But there are significant differences between \ilc{HSJ, DeepFool, D-DeepFool} on \textit{benign flag} as we have tested the $95 \%$ of $E_{\ilc{HSJ}} - E_{\ilc{FGSM}} = 0$ (second smallested difference on \textit{benign flag}) to be \ilc{(0.22750277615440784, 0.3084972238455922)} on \textit{benign flag}.
+We think this can be better explained by investigating the [\figurename{\ \ref{bd_minist_budget}}] graph.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.8\textwidth]{{fig/bd_minist_budget.png}}
+    \caption{Budget comparision evasion attack algorithms v. \ilc{Binary Input Detector} on \textit{MINIST}}
+    \label{bd_minist_budget}
+\end{figure}
+
+By investigating the [\figurename{\ \ref{bd_minist_budget}}] graph, it can be tell there is a clearly correlation between the \textit{pertubation budget} and the \textit{adversarial flag} or \textit{benign flag} (e.g., \ilc{D-DeepFool}).
+This is in fact very intuitive as less \textit{pertubation budget}  means the generated adversarial examples have perserved more semantics or their benign origins, thus making \ilc{BID} hard to distinguish wheather an example is benign or not.
+
+However, it remainds unknow why \ilc{D-DeepFool} has a much lesser \textit{benign flag} and \textit{adversarial flag} in comparision to \ilc{DeepFool}. David please have some input here thanks.
+
+\begin{figure}[H]
+\minipage{0.6\textwidth}
+    \includegraphics[width=0.8\textwidth]{{fig/bd_cifar10_acc.png}}
+    \caption{Effectiveness comparision}
+    \label{bd_cifar10_acc}
+\endminipage\hfill
+\minipage{0.6\textwidth}
+    \includegraphics[width=0.8\textwidth]{{fig/bd_cifar10_budget.png}}
+    \caption{Budget comparision}
+    \label{bd_cifar10_budget}
+\endminipage
+\caption*{Evasion attack algorithms v. \ilc{Binary Input Detector} on \textit{CIFAR-10}}
+\end{figure}
+
+Our discovary continues uphold on the \textit{CIFAR-10} dataset as algorithms with lower \textit{pertubation budget} gets flagged less (regardless adversarial or benign).
+
+However, this time it is \ilc{I-FGSM} and \ilc{HSJ} having the least \textit{pertubation budget}.
+This is in fact resonable due to their iterative nature.
+We looked into our experiment and realized it is because \ilc{HSJ} was running on a test set of $250$ examples\footnote{We have to reduce the size as \ilc{BID} needs to generate the adversarial images twices}, in combinations with \ilc{max\_iter = 8}, the algorithm might not have enough iterations and random move to detect the decision boundaries of \textit{MINIST}, which can be a lot harder to detect as they all have pure-color backgrounds.
+
+\subsubsection{Pre-processor}
+
+\begin{figure}[H]
+
+\minipage{0.6\textwidth}
+    \includegraphics[width = 0.8\textwidth]{{fig/ss_minist_acc.png}}
+    \caption{Effectiveness comparision}
+    \label{ss_minist_acc}
+\endminipage\hfill
+\minipage{0.6\textwidth}
+    \includegraphics[width = 0.8\textwidth]{{fig/ss_minist_budget.png}}
+    \caption{Budget comparision}
+    \label{ss_minist_budget}
+\endminipage
+\caption*{Evasion attack algorithms v. \ilc{Spatial Smoothing} on \textit{MINIST}}
+\end{figure}
+
+\begin{figure}[H]
+
+\minipage{0.6\textwidth}
+    \includegraphics[width = 0.8\textwidth]{{fig/ss_cifar10_acc.png}}
+    \caption{Effectiveness comparision}
+    \label{ss_cifar10_acc}
+\endminipage\hfill
+\minipage{0.6\textwidth}
+    \includegraphics[width = 0.8\textwidth]{{fig/ss_cifar10_budget.png}}
+    \caption{Budget comparision}
+    \label{ss_cifar10_budget}
+\endminipage
+\caption*{Evasion attack algorithms v. \ilc{Spatial Smoothing} on \textit{CIFAR-10}}
+\end{figure}
+
+\ilc{Spatial Smoothing} a.k.a.
+\ilc{SS} is our implemented defense algorithm to increase model's robustness against adversarial input -- as it actually actually help predicting the true label of an adversarial image.
+We may proudly say that there is a $38 \%$ \textit{accuracy} before and after the \ilc{SS} being implemented across our four experimented algorithms (we exclude \ilc{D-DeepFool} for this disscussion as it performs identical to standard \ilc{DeepFool}) on \textit{MINIST}.
+
+Note this experiment also confirms the fact that \ilc{HSJ} is probably not ``converged'' yet with its current setting on \textit{MINIST}, as it has again costed high \textit{perturbation budget}.
+We also observed the higher the \textit{pertubation budget}, the better the defensive effectiveness -- this is again in accordance with out intuition as we as human can also distinguish highly perturbed picture well.\newline
+
+Also note  [\figurename{\ \ref{bd_minist_budget}}] seems to be suggesting low \textit{pertubation budget} will result in high model effectiveness, this is only semi-true as the overall effectiveness increase on \textit{CIFAR-10} is comparatively low (only $+6.5 \%$ among the $4$ experimented algorithms, where it is $+38 \%$ in \textit{MINIST}), so it is more of \ilc{SS} being effective against \ilc{HSJ}.
+
+We believe this have something to do with the fact \ilc{SS} look into the activations of neuros of adversarial pattern and either force-zero or oppress them.
+As \ilc{HSJ} being on the decisions boundaries (implied by the low \textit{pertubation budget}), a \ilc{HSJ}-generated adversarial imag might be considered to have adversarial patterns of many kinds and therefore being detected by the defense algorithm.
+
+Minyang, please correct me if I am wrong and add some insight.
+
+\subsubsection{Transformer}\label{defense_transformer}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.8\textwidth]{{fig/nc_backdoor_acc_budget.png}}
+    \caption{\ilc{Backdoor} v. \ilc{Neural Cleanse}}
+    \label{nc_backdoor_acc_budget}
+\end{figure}
+
+Minyang please explain why this works.
+
+\subsubsection{Conclusion}
+
+As each defensive algorithms have their different purposes and propertities, it is hard to conclude them generally.
+But base on our consistent observation, it might be safe to say an adversarial example with less \textit{budger pertubation} is likely likely to be detected by a defensive algorithm -- which is consistent to our intuition and the geometrical stucture of feature space and decision boundaries: as if something is the middle of several boundaries, it will be hard to distinguish wheather it is an adversarial example of just an ``outliner'' of a neighborhood class.
+
+In a partical sense, it might be best
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\section{References}
+\nocite{*}
+\raggedright
+\bibliography{references.bib}
+\bibliographystyle{plain}
 

### 2020-12-04 report/article.tex
current progress on individual paper

--- 2020-12-04 report/article.tex
@@
 
-\section{Introduction}
+\renewcommand{\abstractname}{Contributions}
+\begin{abstract}
+We as a group of five have looked into the field of adversarial machine learning and specifically investigated several algorithms regarding aspects of attack (evasion, poisoning) and defense (detector, transformer, pre-process).
+Inside the group, overall contribution are as following:
+\begin{itemize}
+    \item Henry:
+    \begin{itemize}
+        \item Read 3 papers on algorithms.
+        \item Implemented 2 algorithms (\ilc{FGSM} and \ilc{Hop Skip Jump}) with 3 extensions.
+        \item Piplined attack algorithms to work with 2 datasets, collected almost all (7 algorithms/useable extensions) attack experiments data (except \ilc{backdoor} and \ilc{one pixel attack}) for the comparative evaluations.
+        \item Piplined and collected experiments data for \ilc{FGSM, Hop Skip Jump, DeepFool} attacks (and their useable extensions) against \ilc{Detector} and \ilc{Spatial Smoothing} defenses on 2 datasets.
+        \item Implemented $L_2$ and $L_{\infty}$ \textit{perturbation budget} to aid comparative evaluation.
+        \item Wrote \textbf{Introduction and Significance} section.
+        \item Plotted all graphs and charts in \textbf{Comparative Study and Discussion}.
+        \item Helped group move forward by making technical decisions, distributing works, setting up deadlines, and facilitating coordination between groupmates.
+    \end{itemize}
+    \item Minyang:
+    \item Alex:
+    \item Austin:
+    \item David:
+\end{itemize}
+\end{abstract}
 
-\section{Shaochen (Henry) Zhong Individual Report}
+\setcounter{tocdepth}{4}
+\vspace{0.5cm}
+{\hypersetup{hidelinks}
+\tableofcontents
+}
 
-\section{Minyang Tie Individual Report}
+\newpage
 
-\section{Alex Useloff Individual Report}
+\section{Introduction and Significance}
 
-\section{Austin Keppers Individual Report}
+\section{Individual Reports}
+
+\subsection{Shaochen (Henry) Zhong's Individual Report}
+\subsubsection{Overview}
+
+\subsubsection{\ilc{Fast Gradient Sign Method}}
+\paragraph{Algorithm Intuition}
+\paragraph{Algorithm Implementation}
+\paragraph{Experiments}
+\paragraph{Evaluation}
+
+\subsubsection{\ilc{Hop Skip Jump}}
+\paragraph{Algorithm Intuition}
+\paragraph{Algorithm Implementation}
+\paragraph{Experiments}
+\paragraph{Evaluation}
+
+\subsubsection{\ilc{Feature Collision}}
+\paragraph{Algorithm Intuition}
+
+\subsection{Minyang Tie's Individual Report}
+
+\subsection{Alex Useloff's Individual Report}
+
+\subsection{Austin Keppers' Individual Report}
 \subfile{individual_reports/agk51}
 
-\section{David Meshnick Individual Report}
+\subsection{David Meshnick's Individual Report}
 
-\section{Algorithm Comparison}
+\section{Comparative Study and Discussion}
+
+\subsection{Overview}
+\subsection{Attack Algorithms}
+\subsubsection{Evasion}
+\subsubsection{Poisoning}
+\subsection{Defense Algorithms}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% \section{References}
+% \nocite{*}
+% \raggedright
+% \bibliography{references.bib}
+% \bibliographystyle{plain}
 

### 2020-12-04 report/individual_reports/dcm101.tex
current progress on individual paper

\documentclass[../article.tex]{subfiles}

\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[superscript,biblabel]{cite}
\DeclareMathOperator*{\E}{\mathbb{E}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\graphicspath{ {./fig/} }

\begin{document}

The main algorithm that I researched for this report was DeepFool, which is an optimized attack method on data for deep neural network classifiers. This technique was first proposed by Moosavi-Dezfooli et al. in their paper, \emph{DeepFool: a simple and accurate method to fool deep neural networks}. The primary attack vector of DeepFool is to introduce instability into a classifier through adversarial perturbations, where minor changes are made to data samples that result in a classifier giving an incorrect output. What distinguishes DeepFool, however, is that it optimizes its attack to have the minimal amount of perturbations applied to the sample data that still tricks a classifier.

\begin{wrapfigure}{r}{0.25\textwidth} %this figure will be at the right
	\centering
	\includegraphics[width=0.25\textwidth]{adv_pert_img.png}
	\caption{\label{fig:Figure 1}Base image (top row). Image perturbed and perturbations by DeepFool (middle row). Image perturbed and perturbations by fast gradient sign method (bottom row).}
\end{wrapfigure}

Adversarial perturbation has seen extensive research outside of DeepFool. First thoroughly explored by Szegedy et al. in 2014, existing research aims to approximate the minimum number of perturbations required to fool a deep neural network classifier. However, their optimization method does not scale to larger datasets. These techniques are often overly-expensive in terms of computation, such as the method Nyugen et al. developed to render a data sample unrecognizable to a human, but convince a classifier to classify it with confidence. Other researchers created a fast gradient step method, which quickly calculate approximately optimal perturbations, but this estimation can be considerably different from a more optimal solution. Figure 1 demonstrates the perturbations created by DeepFool and those created by the previously-mentioned 'fast gradient step' method. The image was originally classified as a whale, and the noise maps in the right column are the perturbations applied to that image in order for the classifier to declare the augmented image as a turtle instead. It can be clearly observed that DeepFool's perturbations are more minimal in quantity and in their affect on the base image, and was able to achieve the same desired misclassification as the gradient step method.

DeepFool's optimized approach to finding the minimal quantity of perturbations stems from the concept of what a perturbation is. First, they defined an adversarial perturbation as the smallest alteration \textit{\textbf{r}} that can change a classifier's estimated label $\hat{k}(x)$ to be the following (ST means "subject to"):

\[\delta(x:\hat{k}) := \min_r||r||_2  ST \hat{k}(x + r) \neq \hat{k}\]

So, let there be some $\hat{k} = sign(f(x))$, where $f(x)$ is an affine, arbitrary, scalar classification function. The robustness of this classifier, or how resistant it is to error, can be expressed as:

\[ \rho_{adversarial} (\hat{k}) = \mathbb{E}_x \frac{\delta(x:\hat{k})}{||x||_2}\]

Here, $\mathbb{E}_x$ represents the expectation over the distribution of all data. With these two expressions, the researchers determined that, as an affine classifier, the distances between points on the classifier's affine hyperplane $w^T x + b = 0$ and its robustness could be determined, and subsequently, so too could the minimum number of perturbations required to cross that threshold. When computed linearly, they derived the expression for that minimum number of permutations as:

\[r_*(x_0) := \argmin ||r||_2 ST sign(f(x_0+r)) \neq sign(f(x_0)) = -\frac{f(x_0)}{||w||_2^2 w}\]

\[\argmin_{r_i} || r_i ||_2 ST f(x_i) + \nabla f(x_i)^T r_i = 0\]

Perturbation $r$ at index $i$ is computed, and then the next $x_{i+1}$ is updated. This continues until the classifier estimator $\hat{k}$ changes, and thus the prediction changes to the intended wrong label.

\begin{wrapfigure}{l}{0.4\textwidth} %this figure will be at the right
	\centering
	\includegraphics[width=0.4\textwidth]{deepfool_multi_class.png}
	\caption{\label{fig:Figure 2}Pseudocode of the mutliclass iteration of the DeepFool adversarial perturbation attack.}
\end{wrapfigure}

The DeepFool adversarial perturbation optimization method was then expanded to cover mutliclass problem spaces. The researchers treated multi-class classification as an aggregation of binary classification problems, of which the best option is selected. They represent this as, for a classification estimator, $\hat{k}(x) = \argmax_{k} f_k(x)$, where it iterates over each $k$ class. For an affine classifier in this case, an arbitrary classification function can be defined as $f(x) = W^Tx + b$, and the minimum amount of perturbations necessary to change its result is:

\[\argmin_{r} ||r||_2 s.t. \exists k: w_k^T(x_0 + r) + b_k \geq w_{\hat{k}(x_0)}^T (x_0+r) + b_{\hat{k}(x_0)}\]

This equality is similar in terms of geometric distance to that of the distance between some point, $x_0$, and the complement of a polyhedron $P$ that contains it. In this situation, polyhedron $P$ represents the geometric space equivalent to the classification estimator output $\hat{k}(x_0)$. This problem was solved for with binary classification, however, and that solution can be modified to cover this problem. By letting $\hat{l}(x_0)$ represent the nearest hyperplane to the boundary of polyhedron $P$, the minimum amount of perturbations can then be calculated as a vector that projects the label onto that hyperplane. The final implementation of this derivation can be seen in Figure 2, which depicts the full mutliclass algorithm for DeepFool.

\end{document}

### 2020-12-04 algos/defensive_distillation.py
Added ability to use hard labels for misclassified examples

@@ -68,12 +68,7 @@ def get_model(parameters, dataset, distilled=False):
 
 def train_model(model, training_dataset, testing_dataset, parameters, distilled=False):
 
-    #if parameters['momentum_decay'] is None:
     momentum=  parameters['momentum']
-    #else:
-        #momentum = tf.keras.optimizers.schedules.InverseTimeDecay(
-        #    parameters['momentum'], parameters['momentum_decay'], parameters['decay_delay'], staircase=True
-        #)
 
     if parameters['learning_rate_decay'] is None:
         learning_rate = parameters['learning_rate']
@@ -101,52 +96,84 @@ def test_model(model, testing_dataset):
 def get_soft_labels(model, dataset):
     return model.predict(dataset.images, verbose=1)
 
-def filter_soft_data_by_result(soft_dataset, hard_labels):
+def filter_soft_data_by_result(soft_dataset, hard_labels, add_wrong_predictions=False):
     predictions = np.argmax(soft_dataset.labels, axis=1)
     correct_predictions = (hard_labels == predictions)
-    return Dataset(soft_dataset.images[correct_predictions], soft_dataset.labels[correct_predictions], False)
+    wrong_predictions = (hard_labels != predictions)
+    if not add_wrong_predictions:
+        return Dataset(soft_dataset.images[correct_predictions], soft_dataset.labels[correct_predictions], False)
+    else:
+        soft_images = soft_data.images[correct_predictions]
+        hard_images = soft_data.images[wrong_predictions]
+        soft_labels = soft_data.labels[correct_predictions]
+        hard_labels = hard_labels[wrong_predictions]
+        images = soft_images.append(hard_images)
+        labels = soft_labels.append(hard_labels)
+        return Dataset(images, labels, False)
+
 
 def convert_to_one_hot(labels, num_classes):
     return np.eye(num_classes)[labels.reshape(-1)]
 
-def get_defensive_distilled_classifier(parameters, raw_training_data, raw_test_data, remove_incorrectly_predicted):
+def get_defensive_distilled_classifier(parameters, raw_training_data, raw_test_data, remove_incorrectly_predicted, replace_with_hard_labels=False):
     training_dataset = Dataset(raw_training_data[0], raw_training_data[1].flatten())
     test_dataset = Dataset(raw_test_data[0], raw_test_data[1])
     model = get_model(parameters, training_dataset)
     train_model(model, training_dataset, test_dataset, parameters)
-    #test_model(model, test_dataset)
[…]

### 2020-12-04 algos/defensive_distillation.py
Added commenting to defensive distillation

@@ -1,3 +1,6 @@
+# Defensive Distillation implemenation for adversarial learning group
+# 
+
 import tensorflow as tf
 import numpy as np
 import json
@@ -7,17 +10,30 @@ from art.attacks.evasion import FastGradientMethod
 from art.estimators.classification import KerasClassifier
 
 class Dataset:
+    """
+    Class to represent a data set
+    Used as a way to combine the images and labels into one class
+    """
 
     def __init__(self, images, labels, divide_images=True):
+
+        # The images need to be converted to floats in order to work with the classifier
         if divide_images:
             self.images = images / 255.0
         else:
             self.images = images
+
+        # An extra dimension needs to be added for greyscale images
         if self.images[0].ndim < 3:
             self.images = self.images.reshape(self.images.shape[0], self.images.shape[1], self.images.shape[2], 1)
         self.labels = labels
 
 class SoftmaxTemperature(tf.keras.layers.Layer):
+    """
+    Custom layer to have a softmax layer with a temperature perameter
+    Temperature determines how close the probabilities are to each
+    Custom temperature value is not used when distilled is true and the classifier is not being trained.
+    """
     
     def __init__(self, temperature, distilled):
         super(SoftmaxTemperature, self).__init__()
@@ -34,18 +50,30 @@ class SoftmaxTemperature(tf.keras.layers.Layer):
         return normalized_output
 
 def get_dataset(dataset_name):
+    """
+    Loads a dataset from keras by name
+    Returns tuple of images and labels in numpy arrays
+    """
     dataset = getattr(tf.keras.datasets, dataset_name.lower())
     return dataset.load_data()
 
 def get_model(parameters, dataset, distilled=False):
+    """
+    Create a convolutional neural network model according to parameters passed
+    parameters is a dictionary of names and values. Look at mnist_dd.json and cifar10_dd.json for field examples
+    distilled will determine whether the temperature is changed when not training
+    """
 
     model = tf.keras.models.Sequential()
+
+    # Create first set of convolutional layers and a pooling layer
     num_conv1_layers = parameters['conv1_layers']
     conv1_filters = parameters['conv1_num_filters']
     model.add(tf.keras.layers.Conv2D(conv1_filters, (3, 3), activation='relu', input_shape=dataset.images[0].shape))
     for i in range(num_conv1_layers - 1):
[…]

### 2020-12-05 report/article.tex
✨ Add introduction and relavent materials.

--- 2020-12-04 report/article.tex
@@
 
-\renewcommand{\abstractname}{Contributions}
-\begin{abstract}
-We as a group of five have looked into the field of adversarial machine learning and specifically investigated several algorithms regarding aspects of attack (evasion, poisoning) and defense (detector, transformer, pre-process).
-Inside the group, overall contribution are as following:
-\begin{itemize}
-    \item Henry:
+\setcounter{tocdepth}{4}
+\vspace{0.5cm}
+{\hypersetup{hidelinks}
+\tableofcontents
+}
+
+\newpage
+
+\section{Introduction and Significance}
+
+In the field of machine learning, it if often taken for granted that the testing examples have no malicious intent -- as it if something is labled to be a \ilc{dog}, it will indeed look like a \ilc{dog}.
+However, with the growing popularity of machine learning, robustness against adversarial attacks has been a more and more important metric.
+Adversarial machine learning is the field studying how to attack a model to make it output incorrect results (e.g., false predictions) in different stage of the model building, and how to make a model more robust against various kinds of attacks.\newline
+
+Here is a classic example of a successful adversarial attack borrowed from Google \cite{cite:google_fgsm}: by applying the middle pertubation to the original image, a supposely Labrador Retriever, while still looks like a Labrador Retriever, is now misclassified as a Weimaraner.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = \textwidth]{{fig/adv_example.png}}
+    \caption{An example of adversarial pertubation resulting successful adversarial attack}
+    \label{adv_example}
+\end{figure}
+
+One explaination\cite{cite:ytb_talk} of why adversarial attack works is because there is a natural distinction between how we read and how machine read into a piece of information.
+When we human are asked to classify between a \textit{dog} from a \textit{cat}, we know to focus on the ears and snout:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.6\textwidth]{{fig/ytb_human.png}}
+    \caption{Human perspective}
+    \label{ytb_human}
+\end{figure}
+
+and we considered the pertubation in [\figurename{\ \ref{adv_example}}] to be meaningless because we cannot digest useful information out of it.
+But that might not be the case to the ``eyes'' of a machine as it has no knowledge about cats and dogs.
+To ``translate'' the machine's perspective to ``human terms,'' how machine look at these cat/dig pictures are probably like the following:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.6\textwidth]{{fig/ytb_machine.png}}
+    \caption{Machine perspective}
+    \label{ytb_machine}
+\end{figure}
+
+In fact, a machine might considers the pertubation in [\figurename{\ \ref{adv_example}}] to be more ``informative'' than the features we care about (ears and snout).
+And since models are set to maximize accuracy as a general goal, it will utilize both features -- both the \textit{robust features} (features that keep being robust after adversarial pertubation), and the \textit{non-robust features} (e.g., some ``noise'' to human):
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.6\textwidth]{{fig/ytb_features.png}}
+    \caption{Robust and non-robust features}
+    \label{ytb_features}
+\end{figure}
+
+Thus, if a model's decision is largly base on these non-robust features, we may apply adversarial pertubations to adjust these features and causing the model to output false results. \newline
+
+For this paper in particular, we will look into \textit{evasion attack} (causing the model to output false result by modifying the input), \textit{poisoning attack} (alter the training set of a model to make it produce inaccruate decision boundaries), and some corresponding defense methods against these attacks.
+
+\section{Individual Reports}
+
+\subsection{Shaochen (Henry) Zhong's Individual Report}
+\subsubsection{Overview}
+
+I have wholeheartedly lead and contributed to this group projects, below is an itemized list of my contributions.
+I have inquired Dr.
+Ray and confirmed they can be considered as ``extra works'' and maybe give me some grade boost.
+Thanks.
 \begin{itemize}
@@
 \end{itemize}
-    \item Minyang:
-    \item Alex:
-    \item Austin:
-    \item David:
-\end{itemize}
-\end{abstract}
-
-\setcounter{tocdepth}{4}
-\vspace{0.5cm}
-{\hypersetup{hidelinks}
-\tableofcontents
-}
-
-\newpage
-
-\section{Introduction and Significance}
-
-\section{Individual Reports}
-
-\subsection{Shaochen (Henry) Zhong's Individual Report}
-\subsubsection{Overview}
 
@@
 \paragraph{Algorithm Intuition}
+
+\ilc{FGSM} is a \textit{white-box} evasion attack algorithm. Being \text{white-box} meaning the attacker was assumed to have access to the internal of the model,
+
 \paragraph{Algorithm Implementation}

### 2020-12-05 report/article.tex
🔨 Compress photo to make them small and speed up LaTeX compile.

@@
 
-I have wholeheartedly lead and contributed to this group projects, below is an itemized list of my contributions.
+I have wholeheartedly lead and contributed to this group project, below is an itemized list of my contributions.
 I have inquired Dr.
-Ray and confirmed they can be considered as ``extra works'' and maybe give me some grade boost.
-Thanks.
+Ray and confirmed these can be considered as ``extra works'' and maybe give me some grade boost.
+Thanks :)
 \begin{itemize}
@@
 
-\ilc{FGSM} is a \textit{white-box} evasion attack algorithm. Being \text{white-box} meaning the attacker was assumed to have access to the internal of the model,
+\ilc{FGSM} is a \textit{white-box} evasion attack algorithm.
+Being \text{white-box} means the attacker is assumed to have access to the internal of the model: the structure, the parameters...
+basically each and every details of the model is considered to be known.
+
+In this case, we mostly care about the \ilc{loss} function of the model.
+The intuition of \ilc{FGSM} is elegent and effective -- in short: gradient ascent.
+Assume we have an benign example $x$ with label $y$, and we are trying to make it adversarial by letting the model classify $x_{\text{adv}}$ to be not $y$.
+We apply the following pertubation on $x$ to achieve an $x_{\text{adv}}$
+
+\begin{equation}
+    x_{\text{adv}} = x + \epsilon \cdot \textit{sign}(\nabla_x J(\theta, x, y))
+\end{equation}
+
+where $J$ is the \ilc{loss} function and $\theta$ is the parameters of the model.
+It is clearly to tell that by finding a proper amount of $\epsilon$, we know $x_{\text{adv}}$ will eventually cross the $y-\neg y$
 

### 2020-12-05 report/article.tex
✨ Finished FGSM for individual report.

@@
 \patchcmd{\thebibliography}{\section*{\refname}}{}{}{}
+
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\definecolor{mauve}{rgb}{0.58,0,0.82}
+
+\lstset{frame=tb,
+  language=Python,
+  aboveskip=3mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=flexible,
+  basicstyle={\small\ttfamily},
+  numbers=none,
+  numberstyle=\tiny\color{gray},
+  keywordstyle=\color{blue},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  breaklines=true,
+  breakatwhitespace=true,
+  tabsize=3
+}
 
@@
 
-\ilc{FGSM} is a \textit{white-box} evasion attack algorithm.
+\ilc{FGSM}\cite{cite:fsgm_paper} is a \textit{white-box} evasion attack algorithm.
 Being \text{white-box} means the attacker is assumed to have access to the internal of the model: the structure, the parameters...
@@
 \begin{equation}
-    x_{\text{adv}} = x + \epsilon \cdot \textit{sign}(\nabla_x J(\theta, x, y))
+    x_{\text{adv}} = x + \epsilon \cdot \text{sign}(\nabla_x J(\theta, x, y))
+    \label{fgsm_eq}
 \end{equation}
@@
 where $J$ is the \ilc{loss} function and $\theta$ is the parameters of the model.
-It is clearly to tell that by finding a proper amount of $\epsilon$, we know $x_{\text{adv}}$ will eventually cross the $y-\neg y$
+It is clearly to tell that by finding a proper amount of $\epsilon$, we know $x_{\text{adv}}$ will eventually cross the $y$ and $\neg y$ decision boundary and be classified as a $\neg y$ object.
+We know this direction will lead to a $\neg y$ space because a model is designed to minimize the \ilc{loss} -- thus it is always doing gradient descent -- and by going against the gradient to do gradient ascent, it will ``maximize'' the \ilc{loss} and eventually be misclassified.
+And if the value of $\epsilon$ is small enough, the $x_{\text{adv}}$ will sill perserve enough semantic from $x$ and thus relatively indistinguishable to human eyes.
+Like the following exmaple in [\figurename{\ \ref{google_panda}}]:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.8\textwidth]{{fig/google_panda.png}}
+    \caption{Applying gradient ascent pertubation to a panda image, $\epsilon = 0.07$}
+    \label{google_panda}
+\end{figure}
+
+Although the $x_{\text{adv}}$ on the RHS has been adversarially altered, because the distance of pertubation is small enough, it sill looks like a panda -- a.k.a.
+perserving the majority semantic of $x$.
+
+\subparagraph{Extension 1: \ilc{Targeted Fast Gradient Sign Method}}
+
+As standard \ilc{FGSM}, assuming implemented on $x$ with $y$-label, only cares about reaching a space of $\neg y$.
+This can be undesired for certain application.
+One scenario maybe is to attack the OCR system of bank checks (which is usually the goal when attacking \textit{MINIST}), the attacker would want a lower valued number to be recognized as a higher valued number (e.g., \ilc{0 -> 9}), but not vice versa.
+Thus, I have implemented a targeted version of \ilc{FGSM}, where instead of doing gradient ascent to $y$ like in [Equation \ref{fgsm_eq}], it does gradient descent towards the label of desired target.\newline
+
+Say we have a target of $x_t$ with label $y_t$, the mathematical intuition of \ilc{T-FGSM} is:
+
+\begin{equation}
+    x_{\text{adv}} = x - \epsilon \cdot \text{sign}(\nabla_x J(\theta, x, y_t))
+    \label{t_fgsm_eq}
+\end{equation}
+
+Note we are back to standard gradient descent like running a normal model.
+This is because we want to minimize the \ilc{loss} of $x_{\text{adv}}$ with label $y_t$ -- which is not guaranteed by randoming doing gradient ascent out of $y$ as that might not be the right direction.
+
+\subparagraph{Extension 2: \ilc{Iterative Fast Gradient Sign Method}}
+
+One major drawback of traditional \ilc{FGSM} is to decide the $\epsilon$ value in [Equation \ref{fgsm_eq}].
+Intuitively, such $\epsilon$ can't be too small, otherwise the applied pertubation will be too small to make $x_{\text{adv}}$ across the $y$ to $\neg y$ decision boundary.
+However, it also can't be too large as it will lose the semantic of $x$, like in the follwing example we applied an $\epsilon = 30$ to the Labrador Retriever in [\figurename{\ \ref{adv_example}}] and this is just pure noise:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.2\textwidth]{{fig/google_fgsm_overshoot.png}}
+    \caption{Perturbed Labrador Retriever with $\epsilon = 30$}
+    \label{google_fgsm_overshoot}
+\end{figure}
+
+In this case, although [\figurename{\ \ref{google_fgsm_overshoot}}] is still an successful adversarial attack to the machine (as it was classified as \textit{Chain Mail} for some reasons).
+The attack is by essence meaningless as it has lost all semantics of a Labrador Retriever -- and we might as well just swap it with an actual chain mail picture and call it a successful attack.\newline
+
+\noindent More important, depending on the decision boundaries of a model, some value of $\epsilon$, altough being large enough, might also fail the attack.
+Consider a model with the following decision boundary:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.3\textwidth]{{fig/overshoot_non_target.png}}
+    \caption{Potential $\epsilon$ overshoot}
+    \label{overshoot_non_target}
+\end{figure}
+
+As demoed in [\figurename{\ \ref{google_fgsm_overshoot}}], with an unfortunate $\epsilon$, even being large, an attack can still fail.
+Thus I took advantage of doing a \textit{white-box} attack and implemented an iterative version of \ilc{FGSM}.
+As instead of taking an \textit{one-shot} pertubation, it takes one and another small pertubations to reach to a decision boundary; once the prediction is changed, it stops applying further pertubations.
+
+The mathematical intuition of this algorithm will be like [Equation \ref{i_fgsm_eq}]
+
+\begin{equation}
+    x_{\text{adv}_{i+1}} = x_{\text{adv}_{i}} + \epsilon_{\text{step}} \cdot \text{sign}(\nabla_x J(\theta, x_{\text{adv}_{i}}, y))
+    \label{i_fgsm_eq}
+\end{equation}
+
+where $\epsilon_{\text{step}} \ll \epsilon$, and we can hard bound the accumulation of $\epsilon_{\text{step}}$ to be less or equal to $\epsilon$ so the algorithm try to perturb an example which is far away from its decision boundary and running forever.
+And since the final $x_{\text{adv}} $ will be right on the decision boundary (granted a small enough $\epsilon_{\text{step}}$ was used), it will perserve a healthy amount of semantics of $x$.
+
+\subparagraph{Extension 3: \ilc{Iterative Targeted Fast Gradient Sign Method}}
+
+Naturally, I combined my two implementation together. [Equation \ref{it_fgsm_eq}] is the mathematical intuition of the algorithm:
+
+\begin{equation}
+    x_{\text{adv}_{i+1}} = x_{\text{adv}_{i}} - \epsilon_{\text{step}} \cdot \text{sign}(\nabla_x J(\theta, x_{\text{adv}_{i}}, y_t))
+    \label{it_fgsm_eq}
+\end{equation}
 
 \paragraph{Algorithm Implementation}
-\paragraph{Experiments}
-\paragraph{Evaluation}
+
+I implemented \ilc{FGSM} and its three extentions with the help of \ilc{ART}\cite{cite:art}.
+It is a \ilc{Python}-based open-source libarary that taken care of the engineering aspects of adversarial machine learning testing.
+Specifically, I used \ilc{ART}'s \ilc{KerasClassifier} to wrap around a pretrained model of \textit{MINIST} and \textit{CIFAR-10} as my victim model -- I can do this because all my implemented algorithms and extensions is attacking a trained model, so how the model was trained is not in my interest of evaluation.\newline
+
+I first gather the \ilc{x\_test} sample set from my dataset, then I feed into the pretained model to get \textit{benign acc} reading. Then I apply the below actiovation methods (by choice)
+
+\begin{lstlisting}
+attacker = FastGradientSignMethod(classifier, eps=0.3, batch_size = 32)
+x_test_adv = attacker.generate(x_test[:num]) # non-targeted
+x_test_adv = attacker.generate_targeted(x_test[:num], x_test[0]) # targeted
+x_test_adv = attacker.generate_iterative(x_test[:num]) # iterative non-targeted
+x_test_adv = attacker.generate_targeted_iterative(x_test[:num], x_test[0]) # iterative targeted
+\end{lstlisting}
+
+to generate the adversarially perturbed \ilc{x\_test\_adv} from \ilc{x\_test}. I then feed \ilc{x\_test\_adv} into the pretained model and collect the \textit{adversarial acc} reading.
+
+In the meantime, I collect $L_2$ and $L_\infty$ distances between a benign and an adversarial images (calculated by channel) to be a mertrics of quantifying \textit{pertubation budget}.
+I also implemented a runtime counter to register how long it took an attack method to run -- you may see them in my following Section \ref{fgsm_exp} and comparative study sections like \ref{attack_algo}.
+
+\paragraph{Experiments and Evaluation}\label{fgsm_exp}
+
+Since I have implemented multiple extensions and \ilc{FGSM} have several params to tone with, I have did a vast amount of experiments. We later decided to go with \ilc{eps = 0.3, eps\_step = 0.05}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 1\textwidth]{{fig/i_fgsm_minist.png}}
+    \caption{\ilc{T-FGSM} and \ilc{IT-FGSM} with $\epsilon = \{ 0.1, 0.3, 0.5\}$ on \textit{MINIST}}
+    \label{i_fgsm_minist}
+\end{figure}
+
+because in [\figurename{\ \ref{google_fgsm_overshoot}}], we may observe the mentioned ``overshooting'' problem as in \ilc{T-FGSM} the \textit{Targeted Acc} is decreasing with $\epsilon$ increasing.
+However, this is sloved by implementing \ilc{IT-FGSM}, the \textit{Targeted Acc} is growing with the $\epsilon$.
+
+Also we noticed we ended with a much better \textit{pertubation budget} in \ilc{IT-FGSM}.
+This is because the algorithm stop pertubation once it reached the target label, thus remain a smaller and therefore preferred $L_2$ and $L_\infty$.
+But we do realize even in \ilc{IT-FGSM}, the $L_2$ and $L_\infty$ is increasing with $\epsilon = 0.3 \rightarrow 0.5$, this is because with a bigger $\epsilon$ the algorithm is trying to move picture that are relatively far away from the target to be the target -- this is undesired the resulted images will likely losing semantics, and it cost more computing power to do so (which is also reflected by the \textit{runtime} data, as it is significantly slower in $\epsilon = 0.5$ than $\epsilon = 0.3$).
+Thus, we set the this to be the parameters of \ilc{FGSM}-related algorithms in comparative studies.
 
 \subsubsection{\ilc{Hop Skip Jump}}
+
+\ilc{HSJ}\cite{cite:hsj_paper} is another evasion attack algorithm I implemented.
+
 \paragraph{Algorithm Intuition}
 \paragraph{Algorithm Implementation}
-\paragraph{Experiments}
-\paragraph{Evaluation}
+\paragraph{Experiments and Evaluation}
 
@@
 With \ilc{HSJ} and \ilc{I-FGSM} being more successful on controlling their perturbation budget -- due to their iterative nature -- and therefore probably are overall more reliable attacks as they can generate more effective (i.e.
-more confuse to a modal) adversarial examples while preserve better semanic of the original benign image (i.e.
+more confuse to a modal) adversarial examples while preserve better semantic of the original benign image (i.e.
 the pertubation is less obvious to human's eyes).

### 2020-12-05 report/individual_reports/dcm101.tex
added personal report and bib folder

@@
 
+\usepackage[
+backend=biber,
+style=alphabetic,
+citestyle=authoryear
+]{biblatex}
+
+\addbibresource{./bib/moosavidezfooli.bib} %Imports bibliography file
+
 \graphicspath{ {./fig/} }
@@
 This technique was first proposed by Moosavi-Dezfooli et al.
-in their paper, \emph{DeepFool: a simple and accurate method to fool deep neural networks}.
+in their paper, \emph{DeepFool: a simple and accurate method to fool deep neural networks} (moosavidezfooli.bib).
 The primary attack vector of DeepFool is to introduce instability into a classifier through adversarial perturbations, where minor changes are made to data samples that result in a classifier giving an incorrect output.
@@
 First thoroughly explored by Szegedy et al.
-in 2014, existing research aims to approximate the minimum number of perturbations required to fool a deep neural network classifier.
+in 2014, existing research aims to approximate the minimum number of perturbations required to fool a deep neural network classifier (szegedy.bib).
 However, their optimization method does not scale to larger datasets.
 These techniques are often overly-expensive in terms of computation, such as the method Nyugen et al.
-developed to render a data sample unrecognizable to a human, but convince a classifier to classify it with confidence.
-Other researchers created a fast gradient step method, which quickly calculate approximately optimal perturbations, but this estimation can be considerably different from a more optimal solution.
+developed to render a data sample unrecognizable to a human, but convince a classifier to classify it with confidence (nyugen.bib).
+Other researchers created a fast gradient step method (goodfellow.bib), which quickly calculate approximately optimal perturbations, but this estimation can be considerably different from a more optimal solution.
 Figure 1 demonstrates the perturbations created by DeepFool and those created by the previously-mentioned 'fast gradient step' method.
@@
 
+The second algorithm that I researched, One Pixel Attack from Vargas et al.'s paper \emph{One Pixel Attack for Fooling Deep Neural Networks}, approched the same concept as DeepFool, but from a much different perspective (vargas.bib).
+While the DeepFool attack method would optimize how many perturbations it needs to an image in order to deceive a classifier, One Pixel Attack aims to determine a single pixel in an image that, when changed, would most likely fool the classifier.
+Additionally, the One Pixel Attack is a semi-black-box attack, where the only data it needs from the classifier are the output probability labels.
+This stands in contrast to the DeepFool attack, which needed access to the classifiers internal functions to best counter them.
+By operating as more of a black-box, where the internal mechanisms of the underlying classifier remain hidden, the One Pixel Attack becomes more versatile, as those data points are easier to access.
+
+As the amount of information available to the One Pixel Attack is limited to its assumptions about the input data and the existing probability labels.
+Vargas et al.
+begin with the problem that for an $n-dimensional$ input, the flattened array of pixels $x$ is the original image that would be properly classified.
+They then propose that the probability of that input image belonging to an arbitrary class $k$ be $f_k(x)$.
+From here, the researchers create a new $n-dimensional$ vector, which holds adversarial perturbations that are defined by:
+
+\[\max_{e(x)^*} f_{a}(x + e(x)) ST ||e(x)||_0 \leq d\]
+
+In this maximizing expression, the perturbations are defined by the original image $x$, the target class $a$, and the small number limit $d$ to which the value can be modified.
+Only a subset of size $d$ dimensions are being modified, and the unaffected perturbations in the new vector $e$ are left to be zero.
+In essence, this allows the One Pixel Attack to radically perturb a small, but significant, portion of the input image.
+These narrow sections are refined by a differential evolution (DE) algorithm, which is a population-based optimization method for multi-part problems.
+As it does not utilize a gradient to theorize about an optimal solution, the DE algorithm does not need to know about the classifier's internal objective functions.
+Instead, it can independently iterate through generations of candidates before reaching what it considers to be most optimal.
+
+I implemented the DeepFool and One Pixel Attack algorithms, along with a custom extension of DeepFool called Dynamic DeepFool.
+The authors of the DeepFool paper, Moosavi-Dezfooli et al., noted that their iteration towards a class boundary was always multiplied by a small constant, $\eta$.
+Furthermore, in my research I came across experiments where several DeepFool attackers
+
+\begin{figure}[H]
+	\begin{tabular} {|p{2cm}|p{2cm}||p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{1.5cm}|}
+		\hline
+		Attack & DataSet  & Accuracy & Precision & Recall & AUC & Loss\\
+		\hline
+		\hline
+		DeepFool & MNIST & 99.3 & 0.993 & 0.993 & 0.997 & 0.0647 \\
+		\hline
+		DeepFool & CFAIR-10 & 0.78.7 & 0.846 & 0.739 & 0.976 & 0.620 \\
+		\hline
+		Dynamic DeepFool & CFAIR-10 & 81.4& 0.864 & 0.766 & 0.980 & 0.549 \\
+		\hline
+		One Pixel Attack & CFAIR-10 & 59.4 & 0.688 & 0.478 & 0.919 & 1.214 \\
+		\hline
+	\end{tabular}
+	\caption{Initial results of classifiers before attacks were applied (control group).}
+	\label{fig:ep0.3}
+\end{figure}
+
+\begin{figure}[H]
+	\begin{tabular}{ |p{2cm}|p{2cm}||p{1.5cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|p{1.5cm}|}
+		\hline
+		Attack & DataSet  & \% Success Rate & Adv Accuracy & Precision & Recall & AUC & Loss\\
+		\hline
+		\hline
+		DeepFool & MNIST & 8.70 & 92.3 & 0.923 &0.922 & 0.967 & 0.9035 \\
+		\hline
+		DeepFool & CFAIR-10 & 87.60 & 19.20 & 0.0563 & 0.03 & 0.746 & 3.783  \\
+		\hline
+		DeepFool & CFAIR-10 & 90.20 & 15.20 & 0.067 & 0.044 & 0.707 & 5.021 \\
+		\hline
+		DeepFool & CFAIR-10 & 92.60 & 14.80 & 0.0937 & 0.066 & 0.688 & 5.257 \\
+		\hline
+		\hline
+		Dynamic DeepFool & CFAIR-10 & 97.60 & 12.20 & 0.060 & 0.034 & 0.730 & 3.938 \\
+		\hline
+		Dynamic DeepFool & CFAIR-10 & 98.60 & 11.60 & 0.072 & 0.052 & 0.690 & 5.571 \\
+		\hline
+		Dynamic DeepFool & CFAIR-10 & 98.40 & 13.40 & 0.063 & 0.042 & 0.709 & 4.564 \\
+		\hline
+		One Pixel Attack & CFAIR-10 & 19.80 & 43.6 & 0.436 & 0.436 & 0.690 & 8.856\\
+		\hline
+		One Pixel Attack & CFAIR-10 & 18.80 & 35.8 & 0.358 & 0.358 & 0.646 & 10.159\\
+		\hline
+	\end{tabular}
+	\caption{Results of attacks on designated datasets.
+Attacks with MNIST were performed with default Keras classifier.
+Attacks with CFAIR-10 were performed with custom Keras classifier, as shown in Figure 5.}
+	\label{fig:ep0.4}
+\end{figure}
+
+\begin{wrapfigure}{l}{0.4\textwidth} %this figure will be at the right
+	\centering
+	\includegraphics[width=0.4\textwidth]{cnn_arch.png}
+	\caption{\label{fig:Figure 5} Architecture of deep neural network used in CFAIR-10 tests.}
+\end{wrapfigure}
+
+\noindent were trained in tandem, with the only difference being their $\eta$ value.
+So, utilizing a principle of gradient descent, I created a version of DeepFool that possessed a dynamical $\eta$ value.
+The value of the learning constant $\eta$ was determined by the following expression: $0.0001 * \log(i + 2)$, where $i$ was the current iteration count.
+Instead of the default value of $10e^6$, $\eta$ would begin larger and rapidly approach its target value.
+Then, its step size would begin to decrease as it approached.
+
+The DeepFool algorithm was tested on both the MNIST and CFAIR-10 datasets, while the Dynamic DeepFool and One Pixel Attack methods were only tested on the CFAIR-10 dataset, which allows for a more direct comparison.
+From the same deep convolutional neural network architecture depicted in Figure 5, three classifiers were generated for each CFAIR-10 test.
+Before any attack was tested, each model was fitted, and their initial average performance is shown in Figure 3.
+The results shown in Figure 4 state the respective model's performance on adversarially-generated test samples, but their training data remained unmodified.
+The "\% Success Rate" column in Figure 4 denotes the percentage of provided adversarial samples that successfully fooled the classifier.
+
+With regards to the MNIST dataset, while there was a noticeable decrease in accuracy, precision, recall, and AUC (as well as an increase in loss), the size of that decrease was inconsistent with all of the CFAIR-10 results, and it remains unclear how consistent it is with the original researchers.
+Moosavi-Dezfooli et al.'s original paper was not concerned with the direct performance metrics of the models which suffered a DeepFool attack, but rather the quantity of perturbations and general robustness of already established algorithms.
+Thus, there is no comparable data to contrast this anomaly with.
+
+With regards to the performance difference between the DeepFool (DF1) and Dynamic DeepFool (DF2), the results demonstrated potential for further refinement.
+While each algorithm was largely successful in their attack on the classifier, DF2 outperformed DF1 in each recorded metric.
+DF2 caused, on average, a greater rate of misclassification than DF1 did.
+An additional difference that may warrant further analysis is the difference in time between DF1 and DF2 to complete an attack.
+If DF2 can reach its boundary faster than DF1, that will result in the conservation of computational resources.
+
+With regards to the One Pixel Attack algorithm, this implementation's results are consistent with those of the original authors.
+Vargas et al.
+recorded a decrease in accuracy by 16.89\%, from 85.6\% to 68.71\% after a non-targeted, one-pixel attack.
+This implementation caused the associated classifier to drop its accuracy by, on average, 19.7\%.
+Considering that the initial accuracy wasn't as high as that recorded in Vargas et.
+al, it is likely that this instance's provided classifier was not as strong, and thus more prone to failure.
+Nevertheless, these results do appear to reconcile with the established literature.
+
+\printbibliography
+
 \end{document}

### 2020-12-05 report/article.tex
added sections in article.txt (mainly in evasion)

@@
 	\subsection{David Meshnick's Individual Report}
+	\subfile(individual_reports/dcm101)
 
@@
 
-We opted to compare \ilc{Fast Gradient Sign Method} (non-targeted, with one-shot and iterative implementions), \ilc{Hop Skip Jump}, \ilc{DeepFool} (and \ilc{Dynamic DeepFool} -- an extension implemented by David) together as they are all the non-targed evasion algorithm we implemented.
+	We opted to compare \ilc{Fast Gradient Sign Method} (non-targeted, with one-shot and iterative implementions), \ilc{Hop Skip Jump}, \ilc{DeepFool} (and \ilc{Dynamic DeepFool} -- an extension implemented by ) together as they are all the non-targed evasion algorithm we implemented.
 We opted to not include \ilc{Backdoor} in this set of comparsion as it evasion attacks were done in the assumption of having a trained model, it doesn't make sense to have posioning -- which can alter the training set of a model -- to be part of the comparsion.
@@
 
-David please explain a bit on DeepFool as why it perturbed a huge amount while performed not so well, and maybe also why its $L_\infty$ is a lot higher than $L_2$.
+	An unexpected observation came from the DeepFool algorithm, which iterated through more perturbations than we had anticipated.
+This came about as a result of DeepFool's deceptively simple nature, as it is effectively a greedy search algorithm.
+While the function's goal is to enact the fewest possible perturbations to confidently disrupt a classifier, its descent along its gradient does not share the same efficiency.
+The base learning rate ended up costing a significant amount of computational resources.
+However, the extension David created may be a possible solution to this problem.
+As elaborated upon in the individual report, the Dynamic DeepFool implements a logarithmically decreasing learning rate, which improves the speed at which the algorithm approaches the class label boundary.
+This allowed it to have a noticeably smaller quantity of perturbation iterations, and also out performing the original DeepFool in terms of attack effectiveness on an undefended learning system.
 
@@
 	The budget analysis [\figurename{\ \ref{attack_cifar10_budget}}] comfirms our thinking as the perturbation budgets are larger acrossed the board in comparision to \textit{MINIST}.
-Also all other observation made from the \textit{MINIST} budget graph [\figurename{\ \ref{attack_minist_budget}}] are also true in this \textit{CIFAR-10} budget graph.
+Also all other observation made from the \textit{MINIST} budget graph [\figurename{\ \ref{attack_minist_budget}}] are also true in this \textit{CIFAR-10} budget graph.''
 
@@
 	\ilc{DeepFool} and \ilc{D-DeepFool} have shown very similar performance across this section of experiments and their performance are considerably lacking both in terms of \textit{adversarial acc} and \textit{perturbation budget}.
-David, please again summarize a bit here.
+However, the relative-simplicity of the algorithm lends itself more easily to modification, as demonstrated by the performance gains of simply altering the learning rate of the methods gradient traversal.
+
+	One last interesting point of comparison lies between white-box algorithms like DeepFool and black-box algorithms like One Pixel Attack.
+The white-box attack method had unrestrained access to the inner parameters of the victim classifier, and was typically highly effective.
+Meanwhile, the black-box attack could only view the inputs and outputs of the victim model, and was not as effective.
+However, the black-box algorithm was less computationally expensive, as well as requiring fewer parameters to act.
+Thus, we believe that further analysis is warranted to explore the trade-offs with regards to metrics such as computational resources and speed, between each method.
 

### 2020-12-05 algos/defensive_distillation/defensive_distillation.py
Removed ability to use hard labels in second training

@@ -1,5 +1,5 @@
 # Defensive Distillation implemenation for adversarial learning group
-# 
+# Author: Austin Keppers
 
 import tensorflow as tf
 import numpy as np
@@ -135,7 +135,7 @@ def get_soft_labels(model, dataset):
 
     return model.predict(dataset.images, verbose=1)
 
-def filter_soft_data_by_result(soft_dataset, hard_labels, add_wrong_predictions=False):
+def filter_soft_data_by_result(soft_dataset, hard_labels):
     """
     Take predictions and filter out examples that were misclassified
     If add_wrong_predictions is set to True will add these back in with hard labels
@@ -147,20 +147,7 @@ def filter_soft_data_by_result(soft_dataset, hard_labels, add_wrong_predictions=
     correct_predictions = (hard_labels == predictions)
     wrong_predictions = (hard_labels != predictions)
 
-    if not add_wrong_predictions:
-        return Dataset(soft_dataset.images[correct_predictions], soft_dataset.labels[correct_predictions], False)
-    else:
-
-        # Separate correct and incorrect predictions
-        soft_images = soft_data.images[correct_predictions]
-        hard_images = soft_data.images[wrong_predictions]
-        soft_labels = soft_data.labels[correct_predictions]
-        hard_labels = hard_labels[wrong_predictions]
-
-        # Combine images and labels back together
-        images = soft_images.append(hard_images)
-        labels = soft_labels.append(hard_labels)
-        return Dataset(images, labels, False)
+    return Dataset(soft_dataset.images[correct_predictions], soft_dataset.labels[correct_predictions], False)
 
 
 def convert_to_one_hot(labels, num_classes):
@@ -169,7 +156,7 @@ def convert_to_one_hot(labels, num_classes):
     """
     return np.eye(num_classes)[labels.reshape(-1)]
 
-def get_defensive_distilled_classifier(parameters, raw_training_data, raw_test_data, remove_incorrectly_predicted, replace_with_hard_labels=False):
+def get_defensive_distilled_classifier(parameters, raw_training_data, raw_test_data, remove_incorrectly_predicted):
     """
     Train a distilled classifier
     First trains a classifier on hard labels and then a classifier on soft labels
@@ -177,7 +164,6 @@ def get_defensive_distilled_classifier(parameters, raw_training_data, raw_test_d
     parameters are the model parameters loaded form a file
     raw training data and raw test data are tuples of numpy arrays of images and then labels
[…]

### 2020-12-05 report/article.tex
✨ Add HSJ and FC to individual report.

--- 2020-12-05 report/article.tex
@@
 
-\paragraph{Algorithm Implementation}
+\paragraph{Algorithm Implementation}\label{fgsm_imp}
 
-I implemented \ilc{FGSM} and its three extentions with the help of \ilc{ART}\cite{cite:art}.
+I implemented \ilc{FGSM} and its three extentions with the help of \ilc{ART}\cite{cite:art} (which has dependency to \ilc{Tensorflow} and \ilc{Keras}).
 It is a \ilc{Python}-based open-source libarary that taken care of the engineering aspects of adversarial machine learning testing.
@@
 \ilc{HSJ}\cite{cite:hsj_paper} is another evasion attack algorithm I implemented.
+However, it is designed to be a \textit{black-box} attack method, as the attacker don't have access to the internal structure of the model, and the attack is therefore conducted base on model's output (it will be better if the model can also output confidence leval, but it work fine with just signs).
 
 \paragraph{Algorithm Intuition}
+
+With the fundamentals introduced, we may jump into the mathematical intuition of \ilc{HSJ}.
+Note this is a brief walk through of how \ilc{HSJ} work, but not necessarily \textit{``why''} as the original paper used many theorem, which we won't go through here.
+
+\begin{align}
+    S(x') &= max_{c \neq C(x)}{F(x')c - F(x')_{C(x)}} \\ \nonumber
+    S(x') > 0 &\Leftrightarrow \arg \max_c F(x') \neq C(x)
+    \label{hsj_s_eq}
+\end{align}
+
+where $S(x')$ is the decision boundary of the example $x'$, $F(x')$ is the probability of $x'$ class, and $C(x)$ is the current class.
+This is saying the model on $C(x)$ is looking at different classes around itself (different $x'$(s)), and take the one different class with with maximum likelyhood.
+Let $S(x')$ represent a succesuflly attack, we will then try to minimize the distance between $d(x', x)$ while making $S(x') > 0$.
+
+This setup is very similar to a targeted \ilc{FGSM}.
+So natually, we want to get to the boundary of the $x$ and $x'$.
+However with no access to \ilc{loss} function, what we can do is to do a \ilc{binary search} between $x$ and $x'$ and make it $x_{\text{new}}$, and then estimate the gradient of $x_{\text{new}}$, move along such estimated gradient for a short step, then do another \ilc{binary search} until $S(x') > 0$.
+
+For the gradient estimation, the author proposed a function of:
+
+\begin{equation}
+    \widetilde{\nabla S}(x', \delta) = \frac{1}{B} \limit \sum^{B}_{b=1} \phi (x' + \delta u_b) u_b
+    \label{hsj_g_est}
+\end{equation}
+
+Where $\phi(x') = \text{sign}(S(x'))$, which we have get by simply asking the model to predict $x'$.
+And $u_b$ are group of random vectors around $x'$.
+We than ignore the random vertors that is close to being parallel to the decision boundary (in the case that a decision boundary is not a plane, close to the tangent of the boundary) -- we may identify them by looking at vectors of similar direction but have different $\phi(x')$ output when added to $x'$.
+Then we look at the leftover random vectors to converge an estimation of the boundary like demoed in [\figurename{\ \ref{hsj_grad}}].
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.6\textwidth]{{fig/hsj_grad.png}}
+    \caption{Using random vectors to estimate boundary \protect{\cite{cite:hsj_talk}}}
+    \label{hsj_grad}
+\end{figure}
+
+Thus, when we find the minimum $x'$ to $x$ with $S(x') > 0$, a black box attack is completed.
+
 \paragraph{Algorithm Implementation}
+
+Again, I implemented \ilc{HSJ} with the help of \ilc{ART}\cite{cite:art} (which has dependency to \ilc{Tensorflow} and \ilc{Keras}), wehere \ilc{ART} is a open-source \ilc{Python} library.
+Since I have no extension for this method, the activation method is simply:
+
+\begin{lstlisting}
+attacker = HopSkipJump(classifier=classifier, targeted=False, norm=np.inf, max_iter=32, max_eval=100, init_eval=10)
+attacker = HopSkipJump(classifier=classifier, targeted=False, norm=np.inf, max_iter=64, max_eval=1000, init_eval=100) # Close to authors' recommended setting
+x_test_adv = attacker.generate(x_test[:adv_num])
+\end{lstlisting}
+
+and the workflow remain the same as Section \ref{fgsm_imp}. The algorithm has pretty much two aspects: \ilc{binary searches}, and gradient estimation
+
+For the former part, the idea is to generate pertubation in the midpoint of $x$ and $x'$, and applying  \ilc{binary searches} to get the $x^k$ and $x^{k+1}$ where $\phi(x^k) = \phi(x_{\text{target}})$ and $\phi(x^{k+1}) \neq \phi(x_{\text{target}})$, then we make $x^k$ to be the final midpoint of these searches.
+For the latter part, we simply generate pertubation of $x' + u_b$, and depending on the $\phi(x' + u_b)$, we add or minius all pertubation together to be the estimated gradient.
+
 \paragraph{Experiments and Evaluation}
 
+\ilc{HSJ} is the most computationally-heavy algorithm amoung our group's implementations, and thus most experiments done on \ilc{HSJ} will be present and discuss in Section \ref{attack_algo}.
+However, we notice the authors are using a rather aggressive params setting of \ilc{max\_iter=64, max\_eval=10000, init\_eval=100}, assuming the high \ilc{max\_eval} is to evalaute more random vectors along the boundary.
+We have tested \ilc{HSJ Rec Params} (\ilc{max\_iter=64, max\_eval=1000, init\_eval=100}) against \ilc{HSJ Fast Params} (\ilc{max\_iter=32, max\_eval=100, init\_eval=10}) and it seems they have very similar performance as demonstrated in [\figurename{\ \ref{hsj_exp}}]
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.8\textwidth]{{fig/hsj_exp.png}}
+    \caption{\ilc{HSJ} running with recommended and fast params setting on \textit{MINIST}}
+    \label{hsj_exp}
+\end{figure}
+
 \subsubsection{\ilc{Feature Collision}}
-\paragraph{Algorithm Intuition}
+
+\ilc{Feature Collision}\cite{cite:fc_paper} is an algorithm I read and understood but did not actually implement, mostly due to time constraint.
+\ilc{Feature Collision} is a \textit{posioning} attack algorithm, which is usually considered to be impartical as it is highly unlikely for an attack to have access to the training phase of a model.
+
+But \ilc{Feature Collision} is implemented with concept of \ilc{clean label}, as not the attack but a third-party will label the ``poisoned'' image.
+This increases the likelihood of the poisoned image entering the training set of the model as it is commom practice to scrape internet for training data.
+
+So, in a general term, \ilc{Feature Collision} \textit{collides} the feature between a base class to a target class, making adversarial example that carrying the semantic the base class but full of the features of the target class.
+Since it is indistinguishable to human eyes, if it enters to training set of a model, the result can be catastrophic like demoed in [\figurename{\ \ref{fc_eff}}].
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.8\textwidth]{{fig/fc_eff.png}}
+    \caption{The result of \ilc{Feature Collision} \protect{\cite{cite:fc_paper}}}
+    \label{fc_eff}
+\end{figure}
+
+In the paper, the author also emphasis the effectiveness of \ilc{Feature Collision} as normally posioning attack will require control of labels or even having adversarial examples in to most or every batch of images, but \ilc{Feature Collision} complete an effective attack even with just one adversarial example -- a legitment \textit{one-shot kill} as named by the authors.
 

### 2020-12-05 report/individual_reports/dcm101.tex
made references better

@@
 
-\usepackage[
-backend=biber,
-style=alphabetic,
-citestyle=authoryear
-]{biblatex}
-
-\addbibresource{./bib/moosavidezfooli.bib} %Imports bibliography file
-
 \graphicspath{ {./fig/} }
@@
 This technique was first proposed by Moosavi-Dezfooli et al.
-in their paper, \emph{DeepFool: a simple and accurate method to fool deep neural networks} (moosavidezfooli.bib).
-The primary attack vector of DeepFool is to introduce instability into a classifier through adversarial perturbations, where minor changes are made to data samples that result in a classifier giving an incorrect output.
+in their paper, \emph{DeepFool: a simple and accurate method to fool deep neural networks}.
+\cite{DBLP:conf/cvpr/Moosavi-Dezfooli16} The primary attack vector of DeepFool is to introduce instability into a classifier through adversarial perturbations, where minor changes are made to data samples that result in a classifier giving an incorrect output.
 What distinguishes DeepFool, however, is that it optimizes its attack to have the minimal amount of perturbations applied to the sample data that still tricks a classifier.
@@
 First thoroughly explored by Szegedy et al.
-in 2014, existing research aims to approximate the minimum number of perturbations required to fool a deep neural network classifier (szegedy.bib).
-However, their optimization method does not scale to larger datasets.
+in 2014, existing research aims to approximate the minimum number of perturbations required to fool a deep neural network classifier.
+\cite{DBLP:journals/corr/SzegedyZSBEGF13} However, their optimization method does not scale to larger datasets.
 These techniques are often overly-expensive in terms of computation, such as the method Nyugen et al.
-developed to render a data sample unrecognizable to a human, but convince a classifier to classify it with confidence (nyugen.bib).
-Other researchers created a fast gradient step method (goodfellow.bib), which quickly calculate approximately optimal perturbations, but this estimation can be considerably different from a more optimal solution.
+developed to render a data sample unrecognizable to a human, but convince a classifier to classify it with confidence.
+\cite{DBLP:journals/corr/NguyenYC14} Other researchers created a fast gradient step method \cite{DBLP:journals/corr/GoodfellowSS14}, which quickly calculate approximately optimal perturbations, but this estimation can be considerably different from a more optimal solution.
 Figure 1 demonstrates the perturbations created by DeepFool and those created by the previously-mentioned 'fast gradient step' method.
@@
 
-The second algorithm that I researched, One Pixel Attack from Vargas et al.'s paper \emph{One Pixel Attack for Fooling Deep Neural Networks}, approched the same concept as DeepFool, but from a much different perspective (vargas.bib).
-While the DeepFool attack method would optimize how many perturbations it needs to an image in order to deceive a classifier, One Pixel Attack aims to determine a single pixel in an image that, when changed, would most likely fool the classifier.
+The second algorithm that I researched, One Pixel Attack from Vargas et al.'s paper \emph{One Pixel Attack for Fooling Deep Neural Networks}, approched the same concept as DeepFool, but from a much different perspective.
+\cite{DBLP:journals/tec/SuVS19} While the DeepFool attack method would optimize how many perturbations it needs to an image in order to deceive a classifier, One Pixel Attack aims to determine a single pixel in an image that, when changed, would most likely fool the classifier.
 Additionally, the One Pixel Attack is a semi-black-box attack, where the only data it needs from the classifier are the output probability labels.
@@
 
+\bibliography{dcm101}
 \printbibliography
-
 \end{document}

### 2020-12-05 report/article.tex

@@
 \subsection{David Meshnick's Individual Report}
+\subfile{individual_reports/dcm101}
 
@@
 
-David please explain a bit on DeepFool as why it perturbed a huge amount while performed not so well, and maybe also why its $L_\infty$ is a lot higher than $L_2$.
+An unexpected observation came from the \ilc{DeepFool} algorithm, which iterated through more perturbations than we had anticipated.
+This came about as a result of DeepFool's deceptively simple nature, as it is effectively a greedy search algorithm.
+While the function's goal is to enact the fewest possible perturbations to confidently disrupt a classifier, its descent along its gradient does not share the same efficiency.
+The base learning rate ended up costing a significant amount of computational resources.
+However, the extension David created may be a possible solution to this problem.
+As elaborated upon in the individual report, the \ilc{Dynamic DeepFool} implements a logarithmically decreasing learning rate, which improves the speed at which the algorithm approaches the class label boundary.
+This allowed it to have a noticeably smaller quantity of perturbation iterations, and also out performing the original DeepFool in terms of attack effectiveness on an undefended learning system.
 
@@
 \ilc{DeepFool} and \ilc{D-DeepFool} have shown very similar performance across this section of experiments and their performance are considerably lacking both in terms of \textit{adversarial acc} and \textit{perturbation budget}.
-David, please again summarize a bit here.
+However, the relative-simplicity of the algorithm lends itself more easily to modification, as demonstrated by the performance gains of simply altering the learning rate of the methods gradient traversal.
+
+One last interesting point of comparison lies between white-box algorithms like \ilc{DeepFool} and black-box algorithms like \ilc{One Pixel Attack}.
+The white-box attack method had unrestrained access to the inner parameters of the victim classifier, and was typically highly effective.
+Meanwhile, the black-box attack could only view the inputs and outputs of the victim model, and was not as effective.
+However, the black-box algorithm was less computationally expensive, as well as requiring fewer parameters to act.
+Thus, we believe that further analysis is warranted to explore the trade-offs with regards to metrics such as computational resources and speed, between each method.
 
@@
 This is in fact very intuitive as less \textit{pertubation budget}  means the generated adversarial examples have perserved more semantics or their benign origins, thus making \ilc{BID} hard to distinguish wheather an example is benign or not.
-
-However, it remainds unknow why \ilc{D-DeepFool} has a much lesser \textit{benign flag} and \textit{adversarial flag} in comparision to \ilc{DeepFool}. David please have some input here thanks.
 

### 2020-12-05 report/article.tex
📦 Add deliverable final report.

@@
 
+\newpage
 \subsection{Minyang Tie's Individual Report}
 
+\newpage
 \subsection{Alex Useloff's Individual Report}
 
+\newpage
 \subsection{Austin Keppers' Individual Report}
-\subfile{individual_reports/agk51}
 
+\newpage
 \subsection{David Meshnick's Individual Report}
-\subfile{individual_reports/dcm101}
 
+\newpage
 \section{Comparative Study and Discussion}
@@
 
-Likewise, we opted to not compare any other algorithm except \ilc{Backdoor} to against \ilc{Neural Cleanse}, as: Minyang please input here.
+Likewise, we opted to not compare any other algorithm except \ilc{Backdoor} to against \ilc{Neural Cleanse}, as unlearning the backdoor by retraining is one of the Neural Cleanse method, the defense of unlearning retraining is depend on the pattern.
+Since the Backdoor algorithm is a pattern attack algorithm, so the comparison between Backdoor and unlearning retraining is the most reasonable part.
+Also, retraining is a is a commonly used defense method, here we just specifically retrain the pattern of backdoor insert.
 
@@
 
-We believe this have something to do with the fact \ilc{SS} look into the activations of neuros of adversarial pattern and either force-zero or oppress them.
-As \ilc{HSJ} being on the decisions boundaries (implied by the low \textit{pertubation budget}), a \ilc{HSJ}-generated adversarial imag might be considered to have adversarial patterns of many kinds and therefore being detected by the defense algorithm.
-
-Minyang, please correct me if I am wrong and add some insight.
+We believe this have something to do with the fact \ilc{SS} set the value of each pixel to be the mean value of the pixels around this pixel and it can make the pixel value become more continuous.
+As \ilc{HSJ} being on the decisions boundaries (implied by the low \textit{pertubation budget}),
+Thus the mean value set by \ilc{SS} can used to vague the boundaries to defense.
 
@@
 
-Minyang please explain why this works.
+\ilc{Neural Cleanse} is our implemented defense algorithm focus on Unlearning the backdoor by retraining，the algorithm is defend by train infected DNN to recognize correct labels.
+Here we specifically retrain the pattern of \ilc{Backdoor} insert as mentioned on Section $3.1.4$.
+Thus Against the \ilc{Backdoor} attack, \ilc{Neural Cleanse} can achieve a very good defense effect.\newline
+By the graph, the Defensive Accuracy is $70.89\%$ (Note we train the whole \textit{MINIST} dataset), which is a very good defence accuracy.
+In this case, we do not want to compare with other attack algorithm, because the essence of Unlearning retraining is to allow the neural network to resist the influence of external patterns, so retraining is to use pattern to modify the data of the test set and then for training，therefore only \ilc{Backdoor} we implemented is pattern attack, that is why we only compare \ilc{Backdoor} to against \ilc{Neural Cleanse} on this section.
 
@@
 But base on our consistent observation, it might be safe to say an adversarial example with less \textit{budger pertubation} is likely likely to be detected by a defensive algorithm -- which is consistent to our intuition and the geometrical stucture of feature space and decision boundaries: as if something is the middle of several boundaries, it will be hard to distinguish wheather it is an adversarial example of just an ``outliner'' of a neighborhood class.
-
-In a partical sense, it might be best
 
